### 2020-08-05 README.Rmd
initial structure

---
title: "Donations' tax in Chile"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Structure of the repo

This repo contains the code of the article entitled _More flexibility reduces social donations_, the main files are:

- [article-elsevier.Rmd](article-elsevier/article-elsevier.Rmd): generates the manuscript
  - [mybibfile.bib](article-elsevier/mybibfile.bib): contains the database of references
- [presentation.Rmd](presentation/presentation.Rmd): reproduces a presentation of the article

### 2020-08-05 article-elsevier/article-elsevier.Rmd
initial structure

---
title: More flexibility reduces social donations
author:
  - name: Sebastián Cea-Echenique
    email: sebastian.cea@pucv.cl
    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
    footnote: 1
  - name: Claudia Toledo
    email: claudia@example.com
    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
#   - name: Cat Memes
#     email: cat@example.com
#     affiliation: Another University
#     footnote: 2
#   - name: Derek Zoolander
#     email: derek@example.com
#     affiliation: Some Institute of Technology
#     footnote: 2
# address:
#   - code: Some Institute of Technology
#     address: Department, Street, City, State, Zip
#   - code: Another University
#     address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
  # - code: 2
    # text: "Equal contribution"
abstract: |
  We exploit a change in tax donations' law to evaluate a change to more flexibility.

journal: "Economics Letters or Journal of Public Economics"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
#linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

<!-- _Text based on elsarticle sample manuscript, see [http://www.elsevier.com/author-schemas/latex-instructions#elsarticle](http://www.elsevier.com/author-schemas/latex-instructions#elsarticle)_ -->

Introduction
==========================

#### Motivation and legal background

Law XX introduced a framework to foster social donations. Several changes to that law were made...

#### Insertion in the Literature

The relation between taxes and social donations has been studied in the recent literature by ...

Empirical strategy
============

We use a differences in differences approach in a panel structure of the data.

References {#references .unnumbered}
==========

### 2020-08-05 README.Rmd
ETL reference

@@
 - [article-elsevier.Rmd](article-elsevier/article-elsevier.Rmd): generates the manuscript
+  - [ETL.R]() prepares the data used in the article
   - [mybibfile.bib](article-elsevier/mybibfile.bib): contains the database of references

### 2020-08-13 BD_modelo.R
Script para generar variables a utilizar en el modelo

@@ -1,0 +1,137 @@
+#script que toma la BD Donaciones_Total y agrega columnas necesarias para generar el modelo 
+
+#### Montos en UTM ####
+#cargar BD
+ScriptsPath_ETL.consolidacion<-paste("/home/",usuario,"/workspace/SxC_ETL/Donaciones/DonacionesFM/Consolidacion/",sep="")
+load(paste(ScriptsPath_ETL.consolidacion,"Donaciones_total_compilado_070820.Rdata",sep=""))
+
+#conservar solo donaciones con rut 
+Donaciones_total<-Donaciones_total[!is.na(Donaciones_total$RUT),] #1.415.469
+
+library(readxl)
+valorUTM <- read_excel("~/workspace/donationstax/valorUTM.xlsx")
+colnames(valorUTM)<-c("Año","Mes","UTM")
+
+sum(is.na(Donaciones_total$Año))#12 observaciones sin año
+sum(is.na(Donaciones_total$Mes))#19 observaciones sin mes
+
+#se quitan donaciones sin año
+Donaciones_total<-Donaciones_total[!is.na(Donaciones_total$Año),] #1.415.457
+sum(is.na(Donaciones_total$Mes))#7 observaciones sin mes
+#para aquellas donaciones con Mes=NA se imputa por Mes=01
+Donaciones_total$Mes<-ifelse(is.na(Donaciones_total$Mes),"01",Donaciones_total$Mes)
+
+Donaciones_total$Año<-as.numeric(Donaciones_total$Año)
+Donaciones_total$Mes<-as.numeric(Donaciones_total$Mes)
+valorUTM$Año<-as.numeric(valorUTM$Año)
+valorUTM$Mes<-as.numeric(valorUTM$Mes)
+
+#Monto en pesos corrientes a UTM
+Donaciones_total<-merge(Donaciones_total,valorUTM,by=c("Año","Mes"),all.x = TRUE)
+sum(is.na(Donaciones_total$UTM)) #43 observaciones con año 2020
+Donaciones_total<-Donaciones_total[!is.na(Donaciones_total$UTM),] #1.415.414
+
+Donaciones_total$MONTO.FONDO.MIXTO<-as.numeric(Donaciones_total$MONTO.FONDO.MIXTO)
+Donaciones_total$MONTO.INSTITUCIÓN<-as.numeric(Donaciones_total$MONTO.INSTITUCIÓN)
[…]

### 2020-08-13 article-elsevier/article-elsevier.Rmd
Actualización del articulo

@@
     footnote: 1
-  - name: Claudia Toledo
-    email: claudia@example.com
+  - name: Claudia Toledo-Aguirre
+    email: claudia@pucv.cl
     affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
@@
 
-Law XX introduced a framework to foster social donations. Several changes to that law were made...
+In Chile donations with social purposes are ruled by the Law 19.885, that establishes a framework to foster social donations, this law has had three major change since his publication in 2003 on the years 2009, 2011 y 2012.
+These changes are mainly related with how the donors can access to the tax benefits.
+The benefits are deductions of income by two ways, the first one a discount as tax credit and the second discounted as an expense necessary to make the donation.
+
+The law 19.885 concerning social donations in Chile in his first version on 2003, establishes a tributary benefit of 50\% of the donation as credit discount and the other 50\% consider as spending to make the donation.
+To receive this benefit the donor must donate a minimum of the 33\% of the donation to the Mixed Fund (MF<!--footnote -->).
+In this version of the law the limit of the donation was 4.5\% of the taxable liquid income and benefit was equally independent of the amount of the donation.
+
+This law was in force since 2006 to 2010 when it was modified by the law 20.316.
+The mayor changes was the elimination of the obligatory of the donation to the MF to receive the tributary benefit.
+As there is no longer need to donate to the MF to perceive a economic benefit but, if some percentage of the donation is made to the MF then the donor have a greater economic benefit.
+And the other change was the possibility from natural people of donate.
+
+In this law, 20.316, the donors perceive the tributary benefit in one or more of this ways:
+
+1.
+If the donation is less that 1000 UTM (UTM<!--footnote -->) the benefit is 50\% as tributary credit and 50\% as spending.
+In the case that the donor is a firm, it must donate at as least two different charitable institutions and the donation for each one has to be less than 700 UTM.
+
+2.	To the donations greater or equal to 1000 UTM, if at least 33\% is donated to the MF the benefit is 50\% as credit and 50\% as spending, otherwise the benefit is 35\% credit and the rest can be discounted as spending.
+
+3.
+If the donor is a firm and already donated 1000 UTM (first option) he can donate others 1000 UTM to projects to treat addictions to drugs and alcohol having a total of 2000 UTM as donation.
+The benefit and conditions for this extra 1000 UTM is the same as the first point.
+
+4.
+To donations greater that 1000 UTM made by firms to projects to treat addictions to drugs and alcohol and with a donation of at least 25\% to the MF, has a benefit of 50\% of credit and 50\% of spending.
+If the donation to the MF is less than 25\% then the benefit is just 40\% credit and 60\% spending.
+
+<!--preguntar por figuras -->
+
+Lately, the law 20.316 on 2011 was modified by the law 20.565 changing administrative details related to the procedures to register the donations that were maid, nevertheless the law 20.900 on 2012 again changes the benefits around the amount of 1000 UTM.
+Again we can identified four main points to resume the economic benefits of the donations:
+
+1. If the donation is less than 1000 UTM then the benefit is 50\% of credit and 50\% of spending.
+
+2.	If the donation is greater than 1000 UTM and of the amount above 1000 UTM at least 33\% of the donation goes to the MF, then the benefit is of 50\% as credit and 50\% spending.
+If the donation to the MF is less thanof 33\% then the benefit of the part above de 1000 UTM are for 35\% credit and 65\% spending.
+
+3.	If the donor makes the first point, he can donate an extra 1000 UTM to projects or programs of prevention or rehabilitation of alcohol or drugs in which case the benefit is 50\% credit and 50\% spending.
+
+4.	For the part of the donation above 1000 UTM, when at least 25\% has been donated to de MF the benefit is 50\% credit and 50\% spending, if the donation to the MF is less than 25\%, then the credit for the amount above 1000 UTM is 40\%, the rest spending.
+
+Finally, the last modification is on April 14 2016, the second version of the law 20.900 modify articles 8 and 9 related to the limitations of donate to politics groups.
+
+A resume of the period of each law is in Table ~\ref{table: Table 1}
+
+\begin{table}[htbp]
+\begin{center}
+\begin{tabular}{|c|c|}
+\hline
+Law & Period of validity \\
+\hline
+19.885 & 2006 to 2009-dec-31 \\  \hline
+20.316 & 2010-jan-01 to 2010-dec-01 \\ \hline
+20.565 & 2011-jan-01 to 2012-feb-07 \\ \hline
+20.900(1) & 2012-feb-08 to 2016-apr-13\\ \hline
+20.900(2) & 2016-apr-14  \\ \hline
+
+\end{tabular}
+\caption{Modifications to Law 19.885}
+\label{tabla: Table 1}
+\end{center}
+\end{table}
 
@@
 
-The relation between taxes and social donations has been studied in the recent literature by ...
+The investigation in this area has been focus mainly in the relationship between the tax deductibility and charitable donations, as an example, Peloza \& Steel (2005) consider tax deductibility as a price for charitable donations, using meta-analysis techniques they estimate the elasticity of charitable giving for the US in four decades.
+
+In this same path, Zampelli \& Yen (2016) Investigate the effect of reducing the tax deductibility in the levels of charitable donations, finding that the elimination of the deduction would reduce the donation in 35%
+
+Almunia, Guceri, Lockwood \& Scharf (2020) estimates the effects of tax incentives on charitable contributions in the UK in 0.3 (considering intensive and extensive margin tax price elasticities) finding that intensive margin price elasticity increases in magnitude with income, while the opposite happens for the extensive-margin elasticity.
+
+Duquette (2019) finds that the behavior of the giving’s mounts through the time are consistent with the changes in the limit of deductibility of the donor adjusted gross income in the US, specifically this two have a positive and significative relation considering or not parameters by cause, by years or both together.
+
+But, the changes in Chile don’t necessary match exactly with these cases, there is a limit of deduction but his changes through time are minors compared to others.
+The mayor changes are related to the monetary limit of donation that determinate the income deductibility.
 
@@
 
+#### Data information
+
+The data used for this investigation is public from the records of The Ministry of Social Development, at the time that this paper is developed there are records from 2009 to 2018 in pdf format with a total of xx observations.
+
+\begin{table}[]
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{ll}
+\hline
+\multicolumn{1}{c}{\textbf{Atributes}} & \multicolumn{1}{c}{\textbf{Description}}                \\ \hline
+Name of the project                    & Name of the project where de donation is made           \\
+Name of the institution or donator     & Institucional name or donator who receive the donation to a specific project     \\
+Name of de donor                       & Name of the donor, it can be a natural person or a firm \\
+RUT                                    & Unique Roll Tributary of each donor                     \\
+Donation to the Mixed Fund             & Amount of the total donation made that goes for the mixed fund (in chilean peso) \\
+Donation to the institution or donator & Amount of the total donation made that goes for the donator (in chilean peso)    \\
+Total donation                         & Sum of the donation made to the MF and to the institution (in chilean peso)      \\
+Date                                   & Date of the donation                                    \\ \hline
+\end{tabular}%
+}
+\end{table}
+
+Each file contains one observation per donation registering different attributes of each donation, more information in Table XX.
+Nevertheless for the investigation we use only data from the period between xxx-xxx as we are going to look for the change of the law 20.565 to 20.900, this contain approximate XX valid observations (footnote que es una observación valida, que tiene los datos de fecha y rut de donatario)
+
+#### Exploratory analysis
+
+As you can see in Figure XX it is plot the donations in time, each vertical line indicates the validity of a law (table XX), we can see that in period xx-xx there is an increase of the donation (number) and a change of the mount of the donation.
+Beside the changes of law related to the benefit of the donation there are also others changes that affect the records, one is the inclusion of the digital certificate that ease the process of donation for possibles donor, making it more easy to receive the donation, this was implemented by some of the greater foundations in the country by 2013-2014.
+other import at change was in the same year related to the obligatorily of inform the minister the donations that was made to each institution, by that, the number of donation registered is more larger in 2014 than in years before.
+
+#### Pannel data regression
+
+We want to study the effect on donations of the change of law of 20.565 to 20.900, the main change is that for the law 20.900 is no longer necessary to donor to at least two different institution an amount minor to 700 UTM (in Section XX number XX) making more easy to receive the economy incentive for donation, in order to that, is it expected that the donations raise (in number) but we don't now for sure what happens with the amount of the donations
+
+The model that we create have the next variables
+
+<!-- tabla con variables the modelo -->
+
+and follow the next pannel structure
+
+<!-- ecuación del modelo -->
+
+the result are the following
+
+<!--tabla con los resultados de panel -->
+
+As we can see...
+
 References {#references .unnumbered}

### 2020-08-18 article-elsevier/article-elsevier.Rmd
Actualización de gráficos y tablas

@@
 Each file contains one observation per donation registering different attributes of each donation, more information in Table XX.
-Nevertheless for the investigation we use only data from the period between xxx-xxx as we are going to look for the change of the law 20.565 to 20.900, this contain approximate XX valid observations (footnote que es una observación valida, que tiene los datos de fecha y rut de donatario)
+Nevertheless for the investigation we use only data from the period between xxx-xxx as we are going to look the effects of the change of the law 20.565 to 20.900, this contain approximate XX valid observations (footnote que es una observación valida, que tiene los datos de fecha y rut de donatario)
 
@@
 
-As you can see in Figure XX it is plot the donations in time, each vertical line indicates the validity of a law (table XX), we can see that in period xx-xx there is an increase of the donation (number) and a change of the mount of the donation.
-Beside the changes of law related to the benefit of the donation there are also others changes that affect the records, one is the inclusion of the digital certificate that ease the process of donation for possibles donor, making it more easy to receive the donation, this was implemented by some of the greater foundations in the country by 2013-2014.
-other import at change was in the same year related to the obligatorily of inform the minister the donations that was made to each institution, by that, the number of donation registered is more larger in 2014 than in years before.
+As you can see in Figure XX it is plot the donations in time, each vertical line indicates the validity of a law (table XX), we can see that in period xx-xx there is an increase of the donation (number) and a change of the amount of the donation.
+Beside the changes of law related to the benefit of the donation there are also others changes that affect the records, one is the inclusion of the digital certificate that ease the process of donation for possibles donors, making it more easy to receive the benefits of the donation, this was implemented by some of the greater foundations in the country by 2013-2014.
+Other important change in the same year was related to the obligatorily of inform to the minister the donations that was made to each institution, by that, the number of donation registered is more larger in 2014 than in years before.
+
+In Table XX there is a descriptive analysis of the donations in each period
+
+```{r, echo = FALSE,message=FALSE,warning = FALSE}
+#cargar base de datos 
+load("~/workspace/donationstax/Donaciones_total_graficos.Rdata")
+library(ggplot2)
+library(lubridate)
+library(stringr)
+
+#grafico con donaciones y cambio de leyes
+ggplot(Donaciones_total, aes(x = Fecha , y = monto_total_UTM)) +
+  # Make points small and semi-transparent since there are lots of them
+  geom_point(size = 0.5, alpha = 0.5) + 
+  # Add vertical line
+  #geom_hline(yintercept=1000, linetype="dashed", color = "red") +
+  geom_vline(xintercept=as.numeric(as.Date("2010-01-01")), linetype="dashed", color = "red") +
+  geom_vline(xintercept=as.numeric(as.Date("2011-01-01")), linetype="dashed", color = "red") +
+  geom_vline(xintercept=as.numeric(as.Date("2012-02-08")), linetype="dashed", color = "red") +
+  geom_vline(xintercept=as.numeric(as.Date("2016-04-14")), linetype="dashed", color = "red") +
+  # Add labels
+  labs(x = "Date", y = "Total donation")+
+  ylim(0,20000)+
+  annotate("text", x = as.Date("2009-08-11"), y = 19000, label = "Law 19885")+
+  annotate("text", x = as.Date("2010-01-01"), y = 17000, label = "Law 20316")+
+  annotate("text", x = as.Date("2011-01-01"), y = 19000, label = "Law 20565")+
+  annotate("text", x = as.Date("2012-02-08"), y = 17000, label = "Law 20900_1")+
+  annotate("text", x = as.Date("2016-04-14"), y = 19000, label = "Law 20900_2")+
+  ggtitle("Donations: Total amount over time")
+
+ggplot(Donaciones_total, aes(x = Fecha , y = monto_institucion_UTM)) +
+  # Make points small and semi-transparent since there are lots of them
+  geom_point(size = 0.5, alpha = 0.5) + 
+  # Add vertical line
+  #geom_hline(yintercept=1000, linetype="dashed", color = "red") +
+  geom_vline(xintercept=as.numeric(as.Date("2010-01-01")), linetype="dashed", color = "red") +
+  geom_vline(xintercept=as.numeric(as.Date("2011-01-01")), linetype="dashed", color = "red") +
+  geom_vline(xintercept=as.numeric(as.Date("2012-02-08")), linetype="dashed", color = "red") +
+  geom_vline(xintercept=as.numeric(as.Date("2016-04-14")), linetype="dashed", color = "red") +
+  # Add labels
+  labs(x = "Date", y = "Donation to institution")+
+  ylim(0,20000)+
+  annotate("text", x = as.Date("2009-08-11"), y = 19000, label = "Law 19885")+
+  annotate("text", x = as.Date("2010-01-01"), y = 17000, label = "Law 20316")+
+  annotate("text", x = as.Date("2011-01-01"), y = 19000, label = "Law 20565")+
+  annotate("text", x = as.Date("2012-02-08"), y = 17000, label = "Law 20900_1")+
+  annotate("text", x = as.Date("2016-04-14"), y = 19000, label = "Law 20900_2")+
+  ggtitle("Donations: Institution amount over time")
+
+ggplot(Donaciones_total, aes(x = Fecha , y = monto_FM_UTM)) +
+  # Make points small and semi-transparent since there are lots of them
+  geom_point(size = 0.5, alpha = 0.5) + 
+  # Add vertical line
+  #geom_hline(yintercept=1000, linetype="dashed", color = "red") +
+  geom_vline(xintercept=as.numeric(as.Date("2010-01-01")), linetype="dashed", color = "red") +
+  geom_vline(xintercept=as.numeric(as.Date("2011-01-01")), linetype="dashed", color = "red") +
+  geom_vline(xintercept=as.numeric(as.Date("2012-02-08")), linetype="dashed", color = "red") +
+  geom_vline(xintercept=as.numeric(as.Date("2016-04-14")), linetype="dashed", color = "red") +
+  # Add labels
+  labs(x = "Date", y = "Donation to Mixed Found")+
+  ylim(0,2500)+
+  annotate("text", x = as.Date("2009-08-11"), y = 2000, label = "Law 19885")+
+  annotate("text", x = as.Date("2010-01-01"), y = 1850, label = "Law 20316")+
+  annotate("text", x = as.Date("2011-01-01"), y = 2000, label = "Law 20565")+
+  annotate("text", x = as.Date("2012-02-08"), y = 1850, label = "Law 20900_1")+
+  annotate("text", x = as.Date("2016-04-14"), y = 2000, label = "Law 20900_2")+
+  ggtitle("Donations: Mixed Found amount over time")
+
+```
+
+```{r, echo = FALSE,message=FALSE,warning = FALSE, results='asis'}
+#load()
+
+load("~/workspace/donationstax/Donaciones_total_graficos.Rdata")
+
+library(knitr)
+library(kableExtra)
+library(dplyr)
+
+Donaciones_total$Ley<-NA
+Donaciones_total$Ley<-ifelse(Donaciones_total$Fecha<"2010-01-01","Law 19885",NA)
+Donaciones_total$Ley<-ifelse(Donaciones_total$Fecha>="2010-01-01" & Donaciones_total$Fecha<"2010-12-31","Law 20316",Donaciones_total$Ley)
+Donaciones_total$Ley<-ifelse(Donaciones_total$Fecha>="2011-01-01" & Donaciones_total$Fecha<"2012-02-07","Law 20565",Donaciones_total$Ley)
+Donaciones_total$Ley<-ifelse(Donaciones_total$Fecha>="2012-02-08" & Donaciones_total$Fecha<"2016-04-13","Law 20900_1",Donaciones_total$Ley)
+Donaciones_total$Ley<-ifelse(Donaciones_total$Fecha>="2016-04-14" & Donaciones_total$Fecha<"2018-12-31","Law 20900_2",Donaciones_total$Ley)
+
+#tabla de donaciones por periodo de ley 
+tabla.ley<-data.frame(matrix(nrow=5,ncol = 7))
+colnames(tabla.ley)<-c("Law","Observations","Median total donation","Median institution donation","Median Mixed Found donation","Number of donors","Number of donee")
+tabla.ley$Law<-c("Law 19885","Law 20316","Law 20565","Law 20900_1","Law 20900_2")
+
+#cantidad de observaciones 
+tabla.ley[1,2]<-nrow(subset(Donaciones_total,Donaciones_total$Ley=="Law 19885"))
+tabla.ley[2,2]<-nrow(subset(Donaciones_total,Donaciones_total$Ley=="Law 20316"))
+tabla.ley[3,2]<-nrow(subset(Donaciones_total,Donaciones_total$Ley=="Law 20565"))
+tabla.ley[4,2]<-nrow(subset(Donaciones_total,Donaciones_total$Ley=="Law 20900_1"))
+tabla.ley[5,2]<-nrow(subset(Donaciones_total,Donaciones_total$Ley=="Law 20900_2"))
+#mediana de monto total, institucion y utm 
+tabla.ley[1,3]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 19885")$monto_total_UTM,na.rm = TRUE)
+tabla.ley[2,3]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 20316")$monto_total_UTM,na.rm = TRUE)
+tabla.ley[3,3]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 20565")$monto_total_UTM,na.rm = TRUE)
+tabla.ley[4,3]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 20900_1")$monto_total_UTM,na.rm = TRUE)
+tabla.ley[5,3]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 20900_2")$monto_total_UTM,na.rm = TRUE)
+
+tabla.ley[1,4]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 19885")$monto_institucion_UTM,na.rm = TRUE)
+tabla.ley[2,4]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 20316")$monto_institucion_UTM,na.rm = TRUE)
+tabla.ley[3,4]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 20565")$monto_institucion_UTM,na.rm = TRUE)
+tabla.ley[4,4]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 20900_1")$monto_institucion_UTM,na.rm = TRUE)
+tabla.ley[5,4]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 20900_2")$monto_institucion_UTM,na.rm = TRUE)
+
+tabla.ley[1,5]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 19885")$monto_FM_UTM,na.rm = TRUE)
+tabla.ley[2,5]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 20316")$monto_FM_UTM,na.rm = TRUE)
+tabla.ley[3,5]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 20565")$monto_FM_UTM,na.rm = TRUE)
+tabla.ley[4,5]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 20900_1")$monto_FM_UTM,na.rm = TRUE)
+tabla.ley[5,5]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 20900_2")$monto_FM_UTM,na.rm = TRUE)
+
+#cantidad de donantes distintos
+tabla.ley[1,6]<-nrow(table(subset(Donaciones_total,Donaciones_total$Ley=="Law 19885")$RUT))
+tabla.ley[2,6]<-nrow(table(subset(Donaciones_total,Donaciones_total$Ley=="Law 20316")$RUT))
+tabla.ley[3,6]<-nrow(table(subset(Donaciones_total,Donaciones_total$Ley=="Law 20565")$RUT))
+tabla.ley[4,6]<-nrow(table(subset(Donaciones_total,Donaciones_total$Ley=="Law 20900_1")$RUT))
+tabla.ley[5,6]<-nrow(table(subset(Donaciones_total,Donaciones_total$Ley=="Law 20900_2")$RUT))
+
+#cantidad de donatarios distintos
+tabla.ley[1,7]<-nrow(table(subset(Donaciones_total,Donaciones_total$Ley=="Law 19885")$DONATARIO))
+tabla.ley[2,7]<-nrow(table(subset(Donaciones_total,Donaciones_total$Ley=="Law 20316")$DONATARIO))
+tabla.ley[3,7]<-nrow(table(subset(Donaciones_total,Donaciones_total$Ley=="Law 20565")$DONATARIO))
+tabla.ley[4,7]<-nrow(table(subset(Donaciones_total,Donaciones_total$Ley=="Law 20900_1")$DONATARIO))
+tabla.ley[5,7]<-nrow(table(subset(Donaciones_total,Donaciones_total$Ley=="Law 20900_2")$DONATARIO))
+
+kable(tabla.ley) %>%
+  kable_styling(bootstrap_options = "striped")
+
+```
 

### 2020-08-18 article-elsevier/article-elsevier.Rmd
Actualización sobre sección del modelo

@@
   ylim(0,2500)+
-  annotate("text", x = as.Date("2009-08-11"), y = 2000, label = "Law 19885")+
+  xlim(as.Date("2008-11-30"),as.Date("2019-01-01"))+
+  annotate("text", x = as.Date("2009-03-11"), y = 2000, label = "Law 19885")+
   annotate("text", x = as.Date("2010-01-01"), y = 1850, label = "Law 20316")+
@@
 
+tabla.ley$`Median total donation`<-round(tabla.ley$`Median total donation`,2)
+tabla.ley$`Median institution donation`<-round(tabla.ley$`Median institution donation`,2)
+tabla.ley$`Median Mixed Found donation`<-round(tabla.ley$`Median Mixed Found donation`,2)
+
 tabla.ley[1,5]<-median(subset(Donaciones_total,Donaciones_total$Ley=="Law 19885")$monto_FM_UTM,na.rm = TRUE)
@@
 kable(tabla.ley) %>%
-  kable_styling(bootstrap_options = "striped")
+  kable_styling(bootstrap_options = "striped", position = "center",font_size = 8)
 
@@
 
-The model that we create have the next variables
+We use a pannel data regression (\ref{eq:1}) in order to study the effect of the change of law on the donations, and follow the next pannel structure
 
-<!-- tabla con variables the modelo -->
+$$\  AI_{i,t}=AMF_{i,t}+AAMF_{i,t}+DL_{i,t}+OD_{i,t}+AAD_{i,t}+AADo_{i,t}+CL_{i}+TD_{i}+DC_{i}+\alpha_{i}+\beta_{t} $$
+Where $\ AI_{i,t}$ is the amount of the donation to the institution/foundation of the donor $\ i$ in the year $\ t$, $\ AMF_{i,t}$ is the amount of the donation to the Mixed Found of the donor $\ i$ in the year $\ t$, $\ AAMF_{i,t}$ is the accumulated amount donated to the Mixed Found until that donation (included) of the donor $\ i$ in the year $\ t$, $\ DL_{i,t}$ is a binary variables that take $\ 1$ if the donor $\ i$ in the year $\ t$ has donor more than 1000 UTM, and 0 otherwise, $\ OD_{i,t}$ is and ordinal variable and take the value of the position in the year of the donation of the donor $\ i$ in the year $\ t$, $\ AAD_{i,t}$ is the total accumulated amount (to Mixed Found and to Institutions) of the donor $\ i$ in the year $\ t$ until that donation (included), $\ AADo_{i,t}$ is the accumulated amount of the donee $\ i$ in the year $\ t$ until that donation (included), $\ CL_{i}$ is a binary variable that take value $\ 1$ if the donation is made in the period of validity of the Law 20900, $\ TD_{i}$ is a binary variable that take value $\ 1$ if the donor is a firm and $\ DC_{i}$ is a binary variable that take value $\ 1$ if the donation is made in the period of validity of the digital certification, finally $\ \alpha _{i}$ and $\ \beta _{t}$ control effects by donor and by time
 
-and follow the next pannel structure
-
-<!-- ecuación del modelo -->
-
-the result are the following
+The result are the following
 

### 2020-08-27 BD_modelo.R
Actualización de procedimiento para generar base de datos

@@ -5,20 +5,21 @@
 ScriptsPath_ETL.consolidacion<-paste("/home/",usuario,"/workspace/SxC_ETL/Donaciones/DonacionesFM/Consolidacion/",sep="")
 load(paste(ScriptsPath_ETL.consolidacion,"Donaciones_total_compilado_070820.Rdata",sep=""))
 
+Donaciones_total<-df2
 #conservar solo donaciones con rut 
-Donaciones_total<-Donaciones_total[!is.na(Donaciones_total$RUT),] #1.415.469
+Donaciones_total<-Donaciones_total[!is.na(Donaciones_total$RUT),] #1.540.636
 
 library(readxl)
 valorUTM <- read_excel("~/workspace/donationstax/valorUTM.xlsx")
 colnames(valorUTM)<-c("Año","Mes","UTM")
 
 sum(is.na(Donaciones_total$Año))#12 observaciones sin año
-sum(is.na(Donaciones_total$Mes))#19 observaciones sin mes
+sum(is.na(Donaciones_total$Mes))#20 observaciones sin mes
 
 #se quitan donaciones sin año
-Donaciones_total<-Donaciones_total[!is.na(Donaciones_total$Año),] #1.415.457
-sum(is.na(Donaciones_total$Mes))#7 observaciones sin mes
-#para aquellas donaciones con Mes=NA se imputa por Mes=01
+Donaciones_total<-Donaciones_total[!is.na(Donaciones_total$Año),] #1.540.624
+sum(is.na(Donaciones_total$Mes))#8 observaciones sin mes
+#para aquellas donaciones con Mes=NA se imputa por Mes=01,son de año 2014 y 2015, no influyen en cambio ley
 Donaciones_total$Mes<-ifelse(is.na(Donaciones_total$Mes),"01",Donaciones_total$Mes)
 
 Donaciones_total$Año<-as.numeric(Donaciones_total$Año)
@@ -29,7 +30,7 @@ valorUTM$Mes<-as.numeric(valorUTM$Mes)
 #Monto en pesos corrientes a UTM
 Donaciones_total<-merge(Donaciones_total,valorUTM,by=c("Año","Mes"),all.x = TRUE)
 sum(is.na(Donaciones_total$UTM)) #43 observaciones con año 2020
-Donaciones_total<-Donaciones_total[!is.na(Donaciones_total$UTM),] #1.415.414
+Donaciones_total<-Donaciones_total[!is.na(Donaciones_total$UTM),] #1.540.581
 
[…]

### 2020-08-27 article-elsevier/article-elsevier.Rmd
Actualización de figuras y graficos

@@
   - name: Claudia Toledo-Aguirre
-    email: claudia@pucv.cl
+    email: claudia.toledo@pucv.cl
     affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
@@
 bibliography: mybibfile.bib
+header-includes:
+   - \usepackage{physics}
+   - \usepackage{amsmath}
+   - \usepackage{tikz}
+   - \usepackage{mathdots}
+   - \usepackage{yhmath}
+   - \usepackage{cancel}
+   - \usepackage{color}
+   - \usepackage{siunitx}
+   - \usepackage{array}
+   - \usepackage{multirow}
+   - \usepackage{amssymb}
+   - \usepackage{gensymb}
+   - \usepackage{tabularx}
+   - \usepackage{booktabs}
+   - \usetikzlibrary{fadings}
+   - \usetikzlibrary{patterns}
+   - \usetikzlibrary{shadows.blur}
+   - \usetikzlibrary{shapes}
+
 #linenumbers: true
@@
 <!-- _Text based on elsarticle sample manuscript, see [http://www.elsevier.com/author-schemas/latex-instructions#elsarticle](http://www.elsevier.com/author-schemas/latex-instructions#elsarticle)_ -->
+
+```{r setup, include=FALSE,echo = FALSE,message=FALSE,warning = FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+knitr::include_graphics
+library(lubridate)
+library(stringr)
+library(dplyr)
+library(ggplot2)
+library(knitr)
+library(kableExtra)
+library(summarytools)
+library(panelr)
+
+load("~/workspace/donationstax/Donaciones_total_graficos.Rdata")
+load("~/workspace/donationstax/iteraciones/Datos_seleccion_modelo.Rdata")
+knitr::opts_chunk$set(fig.width=5, fig.height=5)
+
+```
 
@@
 
-The law 19.885 concerning social donations in Chile in his first version on 2003, establishes a tributary benefit of 50\% of the donation as credit discount and the other 50\% consider as spending to make the donation.
-To receive this benefit the donor must donate a minimum of the 33\% of the donation to the Mixed Fund (MF<!--footnote -->).
+The law 19.885 (Fig (\ref{fig:law 19885})) concerning social donations in Chile in his first version on 2003, establishes a tributary benefit of 50\% of the donation as credit discount and the other 50\% consider as spending to make the donation.
+To receive this benefit the donor must donate a minimum of the 33\% of the donation to the Mixed Fund (MF^[It is a Fund created by the Law on Donations with Social Purposes to support initiatives that civil society organizations present and that directly benefit people in poverty and / or people with disabilities.
+The Fund's resources come from donations from companies and individuals.
+Fund resources must be distributed through public tenders.
+Ministry of social development and family]).
 In this version of the law the limit of the donation was 4.5\% of the taxable liquid income and benefit was equally independent of the amount of the donation.
+
+\tikzset{every picture/.style={line width=0.75pt}} 
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\centering
+\label{fig:law 19885}
+\draw  [draw opacity=0][fill={rgb, 255:red, 194; green, 195; blue, 196 }  ,fill opacity=0.56 ] (81.23,63.8) ..
+controls (81.23,62.25) and (82.48,61) ..
+(84.03,61) -- (252.7,61) ..
+controls (254.25,61) and (255.5,62.25) ..
+(255.5,63.8) -- (255.5,72.2) ..
+controls (255.5,73.75) and (254.25,75) ..
+(252.7,75) -- (84.03,75) ..
+controls (82.48,75) and (81.23,73.75) ..
+(81.23,72.2) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 61; green, 151; blue, 237 }  ,fill opacity=0.38 ] (81.5,49.28) ..
+controls (81.5,47.8) and (82.7,46.6) ..
+(84.18,46.6) -- (164.82,46.6) ..
+controls (166.3,46.6) and (167.5,47.8) ..
+(167.5,49.28) -- (167.5,57.32) ..
+controls (167.5,58.8) and (166.3,60) ..
+(164.82,60) -- (84.18,60) ..
+controls (82.7,60) and (81.5,58.8) ..
+(81.5,57.32) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 242; green, 152; blue, 65 }  ,fill opacity=0.38 ] (167.5,49.28) ..
+controls (167.5,47.69) and (168.79,46.4) ..
+(170.38,46.4) -- (250.25,46.4) ..
+controls (251.84,46.4) and (253.13,47.69) ..
+(253.13,49.28) -- (253.13,57.92) ..
+controls (253.13,59.51) and (251.84,60.8) ..
+(250.25,60.8) -- (170.38,60.8) ..
+controls (168.79,60.8) and (167.5,59.51) ..
+(167.5,57.92) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.38 ] (81.23,78.8) ..
+controls (81.23,76.84) and (82.82,75.25) ..
+(84.78,75.25) -- (128.95,75.25) ..
+controls (130.91,75.25) and (132.5,76.84) ..
+(132.5,78.8) -- (132.5,89.45) ..
+controls (132.5,91.41) and (130.91,93) ..
+(128.95,93) -- (84.78,93) ..
+controls (82.82,93) and (81.23,91.41) ..
+(81.23,89.45) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (255.19,37.21) -- (255.31,84.39) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (132.49,63.5) -- (132.51,94.1) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (131.95,93) -- (162.37,93.74) ;
+\draw [shift={(166.37,93.83)}, rotate = 181.39] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (81.5,61) -- (252.25,60.8) ;
+\draw [shift={(255.25,60.8)}, rotate = 539.9300000000001] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
+
+\draw (51.67,59.33) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
+\draw (125,53.5) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
+\draw (210.31,52.6) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
+\draw (260.67,27.83) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
+\draw (106.87,83.48) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 33\% MF}}};
+\end{tikzpicture}
 
@@
 1.
-If the donation is less that 1000 UTM (UTM<!--footnote -->) the benefit is 50\% as tributary credit and 50\% as spending.
+If the donation is less that 1000 UTM^[Monthly Tax Unit ("Unidad Tributaria Mensual" in spanish): Unit defined in Chile that corresponds to an amount of money expressed in pesos and determined by law, which is permanently updated by the Consumer Price Index and is used as a tax measure.
+SII, Basic Tax Accounting Dictionary] the benefit is 50\% as tributary credit and 50\% as spending.
 In the case that the donor is a firm, it must donate at as least two different charitable institutions and the donation for each one has to be less than 700 UTM.
 
+\tikzset{every picture/.style={line width=0.75pt}}
+
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (66.61,55.57) ..
+controls (66.61,54.26) and (67.67,53.2) ..
+(68.98,53.2) -- (238.74,53.2) ..
+controls (240.05,53.2) and (241.11,54.26) ..
+(241.11,55.57) -- (241.11,62.68) ..
+controls (241.11,63.98) and (240.05,65.04) ..
+(238.74,65.04) -- (68.98,65.04) ..
+controls (67.67,65.04) and (66.61,63.98) ..
+(66.61,62.68) -- cycle ;
+\draw   (238.5,66.84) .. controls (190.77,71.51) and (162.13,76.18) .. (152.58,80.84) .. controls (143.04,76.18) and (114.4,71.51) .. (66.67,66.84) ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (152.92,41.68) ..
+controls (152.92,40.09) and (154.21,38.8) ..
+(155.8,38.8) -- (237.74,38.8) ..
+controls (239.33,38.8) and (240.62,40.09) ..
+(240.62,41.68) -- (240.62,50.32) ..
+controls (240.62,51.91) and (239.33,53.2) ..
+(237.74,53.2) -- (155.8,53.2) ..
+controls (154.21,53.2) and (152.92,51.91) ..
+(152.92,50.32) -- cycle ;
+%Straight Lines [id:da16254432206470004] 
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (242.5,31.84) -- (242.5,75.84) ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 61; green, 151; blue, 237 }  ,fill opacity=0.38 ] (66.92,42.28) ..
+controls (66.92,40.8) and (68.12,39.6) ..
+(69.6,39.6) -- (150.24,39.6) ..
+controls (151.72,39.6) and (152.92,40.8) ..
+(152.92,42.28) -- (152.92,50.32) ..
+controls (152.92,51.8) and (151.72,53) ..
+(150.24,53) -- (69.6,53) ..
+controls (68.12,53) and (66.92,51.8) ..
+(66.92,50.32) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (67.03,53.3) -- (239.5,51.87) ;
+\draw [shift={(242.5,51.84)}, rotate = 539.52] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
+
+\draw (44,16) node   [align=left] {{\fontfamily{ptm}\selectfont Case 1.}};
+\draw (37.33,51) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
+\draw (279.33,49) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 1000 U.T.M.}}};
+\draw (156.33,101) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small Sets of donation to at least 2 differents institutions }}\\{\fontfamily{ptm}\selectfont {\small with each donation below 700 UTM}}};
+\draw (109.92,46.3) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
+\draw (196.77,44) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
+\draw (247.33,21) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
+\\*
+\end{tikzpicture}
+
 2.	To the donations greater or equal to 1000 UTM, if at least 33\% is donated to the MF the benefit is 50\% as credit and 50\% as spending, otherwise the benefit is 35\% credit and the rest can be discounted as spending.
+
+\tikzset{every picture/.style={line width=0.75pt}}
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.33 ] (61.8,68.97) ..
+controls (61.8,67.33) and (63.13,66) ..
+(64.77,66) -- (113.53,66) ..
+controls (115.17,66) and (116.5,67.33) ..
+(116.5,68.97) -- (116.5,77.88) ..
+controls (116.5,79.51) and (115.17,80.84) ..
+(113.53,80.84) -- (64.77,80.84) ..
+controls (63.13,80.84) and (61.8,79.51) ..
+(61.8,77.88) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (62.2,55.73) ..
+controls (62.2,54.31) and (63.35,53.16) ..
+(64.77,53.16) -- (231.64,53.16) ..
+controls (233.06,53.16) and (234.21,54.31) ..
+(234.21,55.73) -- (234.21,63.43) ..
+controls (234.21,64.85) and (233.06,66) ..
+(231.64,66) -- (64.77,66) ..
+controls (63.35,66) and (62.2,64.85) ..
+(62.2,63.43) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (147.92,41.28) ..
+controls (147.92,39.61) and (149.27,38.26) ..
+(150.94,38.26) -- (230.99,38.26) ..
+controls (232.66,38.26) and (234.01,39.61) ..
+(234.01,41.28) -- (234.01,50.33) ..
+controls (234.01,51.99) and (232.66,53.34) ..
+(230.99,53.34) -- (150.94,53.34) ..
+controls (149.27,53.34) and (147.92,51.99) ..
+(147.92,50.33) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (235.42,33.26) -- (235.5,72.84) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (116.42,53.39) -- (116.58,84.55) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (115.53,83.84) -- (141.14,84.23) ;
+\draw [shift={(145.14,84.29)}, rotate = 180.87] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.33 ] (60.8,139.97) ..
+controls (60.8,138.33) and (62.13,137) ..
+(63.77,137) -- (112.53,137) ..
+controls (114.17,137) and (115.5,138.33) ..
+(115.5,139.97) -- (115.5,148.88) ..
+controls (115.5,150.51) and (114.17,151.84) ..
+(112.53,151.84) -- (63.77,151.84) ..
+controls (62.13,151.84) and (60.8,150.51) ..
+(60.8,148.88) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (60.46,127.37) ..
+controls (60.46,125.97) and (61.59,124.84) ..
+(62.99,124.84) -- (232.23,124.84) ..
+controls (233.62,124.84) and (234.75,125.97) ..
+(234.75,127.37) -- (234.75,134.95) ..
+controls (234.75,136.34) and (233.62,137.47) ..
+(232.23,137.47) -- (62.99,137.47) ..
+controls (61.59,137.47) and (60.46,136.34) ..
+(60.46,134.95) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (235.42,108.26) -- (235.58,139.43) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (115.42,124.39) -- (115.58,155.55) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (114.73,157.38) -- (85.33,156.9) ;
+\draw [shift={(81.33,156.83)}, rotate = 360.94] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 61; green, 151; blue, 237 }  ,fill opacity=0.38 ] (61.92,42.28) ..
+controls (61.92,40.8) and (63.12,39.6) ..
+(64.6,39.6) -- (145.24,39.6) ..
+controls (146.72,39.6) and (147.92,40.8) ..
+(147.92,42.28) -- (147.92,50.32) ..
+controls (147.92,51.8) and (146.72,53) ..
+(145.24,53) -- (64.6,53) ..
+controls (63.12,53) and (61.92,51.8) ..
+(61.92,50.32) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 61; green, 151; blue, 237 }  ,fill opacity=0.38 ] (61.21,112.62) ..
+controls (61.21,111.07) and (62.47,109.82) ..
+(64.02,109.82) -- (127.69,109.82) ..
+controls (129.24,109.82) and (130.5,111.07) ..
+(130.5,112.62) -- (130.5,121.04) ..
+controls (130.5,122.59) and (129.24,123.84) ..
+(127.69,123.84) -- (64.02,123.84) ..
+controls (62.47,123.84) and (61.21,122.59) ..
+(61.21,121.04) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (130.5,112.55) ..
+controls (130.5,110.85) and (131.88,109.47) ..
+(133.57,109.47) -- (230.23,109.47) ..
+controls (231.92,109.47) and (233.3,110.85) ..
+(233.3,112.55) -- (233.3,121.77) ..
+controls (233.3,123.47) and (231.92,124.84) ..
+(230.23,124.84) -- (133.57,124.84) ..
+controls (131.88,124.84) and (130.5,123.47) ..
+(130.5,121.77) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (61.03,124.3) -- (232.5,123.85) ;
+\draw [shift={(235.5,123.84)}, rotate = 539.85] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (62.03,53.3) -- (233.5,52.85) ;
+\draw [shift={(236.5,52.84)}, rotate = 539.85] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
+\draw (104.92,47.3) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
+\draw (190.96,45.8) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
+\draw (240.33,25) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
+\draw (89.22,73) node  [font=\small] [align=left] {{\small {\fontfamily{ptm}\selectfont 33\% MF}}};
+\draw (279.33,123) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small > 1000 U.T.M.}}};
+\draw (96.21,116.52) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 35\% Credit}}};
+\draw (179.26,116.01) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 75\% Expense}}};
+\draw (239.33,102) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
+\draw (87.22,144) node  [font=\small] [align=left] {{\small {\fontfamily{ptm}\selectfont 33\% MF}}};
+\draw (277.33,52) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  > 1000 U.T.M.}}};
+\draw (35.33,53) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
+\draw (33,125) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
+\draw (43,18) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont Case 2.}};
+\end{tikzpicture}
 
@@
 
+\tikzset{every picture/.style={line width=0.75pt}} 
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (79.03,69.3) -- (233.5,68.85) ;
+\draw [shift={(236.5,68.84)}, rotate = 539.8299999999999] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (79,71.57) ..
+controls (79,70.15) and (80.15,69) ..
+(81.57,69) -- (230.93,69) ..
+controls (232.35,69) and (233.5,70.15) ..
+(233.5,71.57) -- (233.5,79.28) ..
+controls (233.5,80.69) and (232.35,81.84) ..
+(230.93,81.84) -- (81.57,81.84) ..
+controls (80.15,81.84) and (79,80.69) ..
+(79,79.28) -- cycle ;
+\draw   (232.5,85) .. controls (189.77,88.95) and (164.13,92.9) .. (155.58,96.84) .. controls (147.04,92.9) and (121.4,88.95) .. (78.67,85) ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (78.88,57.3) ..
+controls (78.88,55.57) and (80.29,54.17) ..
+(82.02,54.17) -- (155.36,54.17) ..
+controls (157.1,54.17) and (158.5,55.57) ..
+(158.5,57.3) -- (158.5,66.71) ..
+controls (158.5,68.44) and (157.1,69.84) ..
+(155.36,69.84) -- (82.02,69.84) ..
+controls (80.29,69.84) and (78.88,68.44) ..
+(78.88,66.71) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (157.65,57.3) ..
+controls (157.65,55.72) and (158.92,54.45) ..
+(160.5,54.45) -- (230.99,54.45) ..
+controls (232.57,54.45) and (233.85,55.72) ..
+(233.85,57.3) -- (233.85,65.86) ..
+controls (233.85,67.43) and (232.57,68.71) ..
+(230.99,68.71) -- (160.5,68.71) ..
+controls (158.92,68.71) and (157.65,67.43) ..
+(157.65,65.86) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (236.42,53.26) -- (236.58,84.43) ;
+\draw (44.33,66) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 1000 U.T.M.}}};
+\draw (280.33,68) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 2000 U.T.M..}}};
+\draw (118.69,62.01) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
+\draw (195.75,60.58) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
+\draw (241.33,43) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
+\draw (52,30) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont Case 3.}};
+\draw (169.33,113) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small Sets of donation to at least 2 differents institutions }}\\{\fontfamily{ptm}\selectfont {\small (differents from Case 1.) with each donation below 700 UTM}}};
+
+\end{tikzpicture}
+
 4.
@@
 
-<!--preguntar por figuras -->
+\tikzset{every picture/.style={line width=0.75pt}} 
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.33 ] (53.8,70.37) ..
+controls (53.8,68.51) and (55.31,67) ..
+(57.17,67) -- (95.13,67) ..
+controls (96.99,67) and (98.5,68.51) ..
+(98.5,70.37) -- (98.5,80.47) ..
+controls (98.5,82.34) and (96.99,83.84) ..
+(95.13,83.84) -- (57.17,83.84) ..
+controls (55.31,83.84) and (53.8,82.34) ..
+(53.8,80.47) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (54,57.77) ..
+controls (54,56.24) and (55.24,55) ..
+(56.77,55) -- (208.73,55) ..
+controls (210.26,55) and (211.5,56.24) ..
+(211.5,57.77) -- (211.5,66.08) ..
+controls (211.5,67.6) and (210.26,68.84) ..
+(208.73,68.84) -- (56.77,68.84) ..
+controls (55.24,68.84) and (54,67.6) ..
+(54,66.08) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (133.08,41.86) ..
+controls (133.08,40.21) and (134.42,38.86) ..
+(136.08,38.86) -- (209.33,38.86) ..
+controls (210.99,38.86) and (212.33,40.21) ..
+(212.33,41.86) -- (212.33,50.86) ..
+controls (212.33,52.52) and (210.99,53.86) ..
+(209.33,53.86) -- (136.08,53.86) ..
+controls (134.42,53.86) and (133.08,52.52) ..
+(133.08,50.86) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (212.42,36.26) -- (212.5,72.84) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (98.42,54.79) -- (98.58,85.95) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (97.13,84.84) -- (122.74,85.23) ;
+\draw [shift={(126.74,85.29)}, rotate = 180.87] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (60.96,128.37) ..
+controls (60.96,126.97) and (62.09,125.84) ..
+(63.48,125.84) -- (207.64,125.84) ..
+controls (209.03,125.84) and (210.16,126.97) ..
+(210.16,128.37) -- (210.16,135.95) ..
+controls (210.16,137.34) and (209.03,138.47) ..
+(207.64,138.47) -- (63.48,138.47) ..
+controls (62.09,138.47) and (60.96,137.34) ..
+(60.96,135.95) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (59.88,111.44) ..
+controls (59.88,109.46) and (61.5,107.84) ..
+(63.48,107.84) -- (118.9,107.84) ..
+controls (120.89,107.84) and (122.5,109.46) ..
+(122.5,111.44) -- (122.5,122.24) ..
+controls (122.5,124.23) and (120.89,125.84) ..
+(118.9,125.84) -- (63.48,125.84) ..
+controls (61.5,125.84) and (59.88,124.23) ..
+(59.88,122.24) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (122.5,112.04) ..
+controls (122.5,110.28) and (123.93,108.84) ..
+(125.7,108.84) -- (206.3,108.84) ..
+controls (208.07,108.84) and (209.5,110.28) ..
+(209.5,112.04) -- (209.5,121.64) ..
+controls (209.5,123.41) and (208.07,124.84) ..
+(206.3,124.84) -- (125.7,124.84) ..
+controls (123.93,124.84) and (122.5,123.41) ..
+(122.5,121.64) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (208.42,107.26) -- (208.5,143.84) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (105.56,127.22) -- (105.73,158.38) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (105.73,158.38) -- (76.33,157.9) ;
+\draw [shift={(72.33,157.83)}, rotate = 360.94] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (53.46,41.46) ..
+controls (53.46,39.73) and (54.87,38.32) ..
+(56.6,38.32) -- (129.95,38.32) ..
+controls (131.68,38.32) and (133.08,39.73) ..
+(133.08,41.46) -- (133.08,50.86) ..
+controls (133.08,52.6) and (131.68,54) ..
+(129.95,54) -- (56.6,54) ..
+controls (54.87,54) and (53.46,52.6) ..
+(53.46,50.86) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.33 ] (60.52,141.59) ..
+controls (60.52,139.72) and (62.03,138.22) ..
+(63.89,138.22) -- (101.86,138.22) ..
+controls (103.72,138.22) and (105.22,139.72) ..
+(105.22,141.59) -- (105.22,151.69) ..
+controls (105.22,153.55) and (103.72,155.06) ..
+(101.86,155.06) -- (63.89,155.06) ..
+controls (62.03,155.06) and (60.52,153.55) ..
+(60.52,151.69) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (61.03,125.3) -- (205.5,124.85) ;
+\draw [shift={(208.5,124.84)}, rotate = 539.8199999999999] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (54.03,54.3) -- (209.5,53.85) ;
+\draw [shift={(212.5,53.84)}, rotate = 539.8399999999999] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
+\draw (29.33,52) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
+\draw (92.07,45.41) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
+\draw (172.71,44.36) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
+\draw (217.33,29) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
+\draw (76.15,75.42) node  [font=\small] [align=left] {{\small {\fontfamily{ptm}\selectfont 25\% FM}}};
+\draw (31.5,123) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
+\draw (255.33,123) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small > 1000 U.T.M.}}};
+\draw (91.19,116.84) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 40\% Credit}}};
+\draw (166,116.84) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 60\% Expense}}};
+\draw (211.33,98) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
+\draw (47,17) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont Case 4.}};
+\draw (82.87,146.64) node  [font=\small] [align=left] {{\small {\fontfamily{ptm}\selectfont 25\% FM}}};
+\draw (257.33,54) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small > 1000 U.T.M.}}};
+\end{tikzpicture}
 
@@
 
+\tikzset{every picture/.style={line width=0.75pt}} 
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (66.4,62.6) ..
+controls (66.4,61.16) and (67.56,60) ..
+(69,60) -- (219.3,60) ..
+controls (220.74,60) and (221.9,61.16) ..
+(221.9,62.6) -- (221.9,70.4) ..
+controls (221.9,71.84) and (220.74,73) ..
+(219.3,73) -- (69,73) ..
+controls (67.56,73) and (66.4,71.84) ..
+(66.4,70.4) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (145.08,47.69) ..
+controls (145.08,46.12) and (146.35,44.86) ..
+(147.91,44.86) -- (218.37,44.86) ..
+controls (219.93,44.86) and (221.19,46.12) ..
+(221.19,47.69) -- (221.19,56.17) ..
+controls (221.19,57.73) and (219.93,59) ..
+(218.37,59) -- (147.91,59) ..
+controls (146.35,59) and (145.08,57.73) ..
+(145.08,56.17) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (219.5,37) -- (220.5,83) ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (65.46,47.46) ..
+controls (65.46,45.73) and (66.87,44.32) ..
+(68.6,44.32) -- (141.95,44.32) ..
+controls (143.68,44.32) and (145.08,45.73) ..
+(145.08,47.46) -- (145.08,56.86) ..
+controls (145.08,58.6) and (143.68,60) ..
+(141.95,60) -- (68.6,60) ..
+controls (66.87,60) and (65.46,58.6) ..
+(65.46,56.86) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (66.03,60.3) -- (217.3,59.03) ;
+\draw [shift={(220.3,59)}, rotate = 539.52] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
+\draw (40.33,58) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
+\draw (257.33,58) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 1000 U.T.M.}}};
+\draw (105.27,52.16) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
+\draw (183.14,51.93) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
+\draw (225.33,25) node   [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
+\draw (40,24) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont Case 1.}};
+\end{tikzpicture}
+
 2.	If the donation is greater than 1000 UTM and of the amount above 1000 UTM at least 33\% of the donation goes to the MF, then the benefit is of 50\% as credit and 50\% spending.
@@
 
+\tikzset{every picture/.style={line width=0.75pt}}
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.33 ] (161.63,63.92) ..
+controls (161.63,62.45) and (162.83,61.26) ..
+(164.3,61.26) -- (204.25,61.26) ..
+controls (205.72,61.26) and (206.92,62.45) ..
+(206.92,63.92) -- (206.92,71.92) ..
+controls (206.92,73.4) and (205.72,74.59) ..
+(204.25,74.59) -- (164.3,74.59) ..
+controls (162.83,74.59) and (161.63,73.4) ..
+(161.63,71.92) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (7,64.32) ..
+controls (7,63) and (8.07,61.92) ..
+(9.4,61.92) -- (158.1,61.92) ..
+controls (159.43,61.92) and (160.5,63) ..
+(160.5,64.32) -- (160.5,71.52) ..
+controls (160.5,72.85) and (159.43,73.92) ..
+(158.1,73.92) -- (9.4,73.92) ..
+controls (8.07,73.92) and (7,72.85) ..
+(7,71.52) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (6.88,51.19) ..
+controls (6.88,49.57) and (8.2,48.26) ..
+(9.82,48.26) -- (80.57,48.26) ..
+controls (82.19,48.26) and (83.5,49.57) ..
+(83.5,51.19) -- (83.5,59.99) ..
+controls (83.5,61.61) and (82.19,62.92) ..
+(80.57,62.92) -- (9.82,62.92) ..
+controls (8.2,62.92) and (6.88,61.61) ..
+(6.88,59.99) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (316.38,36.73) -- (315.85,83.91) ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (83.5,51.52) ..
+controls (83.5,50.09) and (84.66,48.92) ..
+(86.1,48.92) -- (157.9,48.92) ..
+controls (159.34,48.92) and (160.5,50.09) ..
+(160.5,51.52) -- (160.5,59.32) ..
+controls (160.5,60.76) and (159.34,61.92) ..
+(157.9,61.92) -- (86.1,61.92) ..
+controls (84.66,61.92) and (83.5,60.76) ..
+(83.5,59.32) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]    (162,37.49) -- (162,91.16)(159,37.49) -- (159,91.16) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (206.5,87.92) -- (207.33,61.26) ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (161.5,49.52) ..
+controls (161.5,47.9) and (162.81,46.59) ..
+(164.43,46.59) -- (235.18,46.59) ..
+controls (236.8,46.59) and (238.12,47.9) ..
+(238.12,49.52) -- (238.12,58.32) ..
+controls (238.12,59.94) and (236.8,61.26) ..
+(235.18,61.26) -- (164.43,61.26) ..
+controls (162.81,61.26) and (161.5,59.94) ..
+(161.5,58.32) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (238.12,49.72) ..
+controls (238.12,48.18) and (239.37,46.92) ..
+(240.92,46.92) -- (312.32,46.92) ..
+controls (313.86,46.92) and (315.12,48.18) ..
+(315.12,49.72) -- (315.12,58.12) ..
+controls (315.12,59.67) and (313.86,60.92) ..
+(312.32,60.92) -- (240.92,60.92) ..
+controls (239.37,60.92) and (238.12,59.67) ..
+(238.12,58.12) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (7.03,62.22) -- (313.12,60.34) ;
+\draw [shift={(316.12,60.32)}, rotate = 539.65] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
+\draw (32,18.92) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small Case 2.}}};
+\draw (45.19,55.59) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
+\draw (122,54.42) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
+\draw (319.33,27.92) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
+\draw (184.27,67.92) node  [font=\footnotesize] [align=left] {{\small {\fontfamily{ptm}\selectfont 33\% FM}}};
+\draw (164.33,28.92) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 1000 U.T.M.}}};
+\draw (30.33,84.92) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
+\draw (276.62,53.92) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
+\draw (199.81,53.92) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
+\end{tikzpicture}
+
 3.	If the donor makes the first point, he can donate an extra 1000 UTM to projects or programs of prevention or rehabilitation of alcohol or drugs in which case the benefit is 50\% credit and 50\% spending.
+
+\tikzset{every picture/.style={line width=0.75pt}} 
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (74.99,47.8) ..
+controls (74.99,46.25) and (76.24,45) ..
+(77.79,45) -- (217.39,45) ..
+controls (218.93,45) and (220.19,46.25) ..
+(220.19,47.8) -- (220.19,56.2) ..
+controls (220.19,57.75) and (218.93,59) ..
+(217.39,59) -- (77.79,59) ..
+controls (76.24,59) and (74.99,57.75) ..
+(74.99,56.2) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (74.7,32.2) ..
+controls (74.7,30.43) and (76.14,29) ..
+(77.9,29) -- (137.3,29) ..
+controls (139.07,29) and (140.5,30.43) ..
+(140.5,32.2) -- (140.5,41.8) ..
+controls (140.5,43.57) and (139.07,45) ..
+(137.3,45) -- (77.9,45) ..
+controls (76.14,45) and (74.7,43.57) ..
+(74.7,41.8) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (140.5,32.55) ..
+controls (140.5,30.83) and (141.89,29.43) ..
+(143.61,29.43) -- (218.39,29.43) ..
+controls (220.11,29.43) and (221.5,30.83) ..
+(221.5,32.55) -- (221.5,41.89) ..
+controls (221.5,43.61) and (220.11,45) ..
+(218.39,45) -- (143.61,45) ..
+controls (141.89,45) and (140.5,43.61) ..
+(140.5,41.89) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (222.5,25) -- (222.58,64.38) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (75.03,45.3) -- (219.5,45.79) ;
+\draw [shift={(222.5,45.8)}, rotate = 180.19] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
+\draw (42.33,43) node   [align=left] {{\fontfamily{ptm}\selectfont {\small 1000 U.T.M.}}};
+\draw (224.33,71) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 2000 U.T.M.}}};
+\draw (107.6,37) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
+\draw (181,37.22) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
+\draw (226.33,19) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
+\draw (27,14) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small Case 3.}}};
+\end{tikzpicture}
 
@@
 
+\tikzset{every picture/.style={line width=0.75pt}} 
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
+\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.33 ] (167.63,171) ..
+controls (167.63,169.53) and (168.83,168.33) ..
+(170.3,168.33) -- (210.25,168.33) ..
+controls (211.72,168.33) and (212.92,169.53) ..
+(212.92,171) -- (212.92,179) ..
+controls (212.92,180.47) and (211.72,181.67) ..
+(210.25,181.67) -- (170.3,181.67) ..
+controls (168.83,181.67) and (167.63,180.47) ..
+(167.63,179) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (13,171.4) ..
+controls (13,170.07) and (14.07,169) ..
+(15.4,169) -- (164.1,169) ..
+controls (165.43,169) and (166.5,170.07) ..
+(166.5,171.4) -- (166.5,178.6) ..
+controls (166.5,179.93) and (165.43,181) ..
+(164.1,181) -- (15.4,181) ..
+controls (14.07,181) and (13,179.93) ..
+(13,178.6) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (12.88,158.27) ..
+controls (12.88,156.65) and (14.2,155.33) ..
+(15.82,155.33) -- (86.57,155.33) ..
+controls (88.19,155.33) and (89.5,156.65) ..
+(89.5,158.27) -- (89.5,167.07) ..
+controls (89.5,168.69) and (88.19,170) ..
+(86.57,170) -- (15.82,170) ..
+controls (14.2,170) and (12.88,168.69) ..
+(12.88,167.07) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (322.38,143.81) -- (321.85,190.99) ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (89.5,158.6) ..
+controls (89.5,157.16) and (90.66,156) ..
+(92.1,156) -- (163.9,156) ..
+controls (165.34,156) and (166.5,157.16) ..
+(166.5,158.6) -- (166.5,166.4) ..
+controls (166.5,167.84) and (165.34,169) ..
+(163.9,169) -- (92.1,169) ..
+controls (90.66,169) and (89.5,167.84) ..
+(89.5,166.4) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]    (168,144.57) -- (168,198.23)(165,144.57) -- (165,198.23) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (212.5,195) -- (188.5,195.86) ;
+\draw [shift={(184.5,196)}, rotate = 357.95] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (212.5,195) -- (213.33,168.33) ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (167.5,156.73) ..
+controls (167.5,155.04) and (168.87,153.67) ..
+(170.57,153.67) -- (223.43,153.67) ..
+controls (225.13,153.67) and (226.5,155.04) ..
+(226.5,156.73) -- (226.5,165.93) ..
+controls (226.5,167.63) and (225.13,169) ..
+(223.43,169) -- (170.57,169) ..
+controls (168.87,169) and (167.5,167.63) ..
+(167.5,165.93) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (226.5,156) ..
+controls (226.5,154.34) and (227.84,153) ..
+(229.5,153) -- (318.12,153) ..
+controls (319.77,153) and (321.12,154.34) ..
+(321.12,156) -- (321.12,165) ..
+controls (321.12,166.66) and (319.77,168) ..
+(318.12,168) -- (229.5,168) ..
+controls (227.84,168) and (226.5,166.66) ..
+(226.5,165) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.33 ] (166.63,75.87) ..
+controls (166.63,74.47) and (167.77,73.33) ..
+(169.17,73.33) -- (201.97,73.33) ..
+controls (203.37,73.33) and (204.5,74.47) ..
+(204.5,75.87) -- (204.5,83.47) ..
+controls (204.5,84.87) and (203.37,86) ..
+(201.97,86) -- (169.17,86) ..
+controls (167.77,86) and (166.63,84.87) ..
+(166.63,83.47) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (12,76.4) ..
+controls (12,75.07) and (13.07,74) ..
+(14.4,74) -- (163.1,74) ..
+controls (164.43,74) and (165.5,75.07) ..
+(165.5,76.4) -- (165.5,83.6) ..
+controls (165.5,84.93) and (164.43,86) ..
+(163.1,86) -- (14.4,86) ..
+controls (13.07,86) and (12,84.93) ..
+(12,83.6) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (11.88,63.27) ..
+controls (11.88,61.65) and (13.2,60.33) ..
+(14.82,60.33) -- (85.57,60.33) ..
+controls (87.19,60.33) and (88.5,61.65) ..
+(88.5,63.27) -- (88.5,72.07) ..
+controls (88.5,73.69) and (87.19,75) ..
+(85.57,75) -- (14.82,75) ..
+controls (13.2,75) and (11.88,73.69) ..
+(11.88,72.07) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (321.38,48.81) -- (320.85,95.99) ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (88.5,63.6) ..
+controls (88.5,62.16) and (89.66,61) ..
+(91.1,61) -- (162.9,61) ..
+controls (164.34,61) and (165.5,62.16) ..
+(165.5,63.6) -- (165.5,71.4) ..
+controls (165.5,72.84) and (164.34,74) ..
+(162.9,74) -- (91.1,74) ..
+controls (89.66,74) and (88.5,72.84) ..
+(88.5,71.4) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]    (167,49.57) -- (167,103.23)(164,49.57) -- (164,103.23) ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (207.5,95) -- (237.5,95) ;
+\draw [shift={(241.5,95)}, rotate = 180] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (207.5,95) -- (207.92,72.13) ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (166.5,61.6) ..
+controls (166.5,59.98) and (167.81,58.67) ..
+(169.43,58.67) -- (240.18,58.67) ..
+controls (241.8,58.67) and (243.12,59.98) ..
+(243.12,61.6) -- (243.12,70.4) ..
+controls (243.12,72.02) and (241.8,73.33) ..
+(240.18,73.33) -- (169.43,73.33) ..
+controls (167.81,73.33) and (166.5,72.02) ..
+(166.5,70.4) -- cycle ;
+\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (243.12,61) ..
+controls (243.12,59.34) and (244.46,58) ..
+(246.12,58) -- (317.12,58) ..
+controls (318.77,58) and (320.12,59.34) ..
+(320.12,61) -- (320.12,70) ..
+controls (320.12,71.66) and (318.77,73) ..
+(317.12,73) -- (246.12,73) ..
+controls (244.46,73) and (243.12,71.66) ..
+(243.12,70) -- cycle ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (13.03,169.3) -- (319.12,167.42) ;
+\draw [shift={(322.12,167.4)}, rotate = 539.65] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
+\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (12.03,74.3) -- (318.12,72.42) ;
+\draw [shift={(321.12,72.4)}, rotate = 539.65] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
+\draw (27,19) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small Case 4.}}};
+\draw (51.19,162.67) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
+\draw (128,161.5) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
+\draw (325.33,135) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
+\draw (190.27,175) node  [font=\footnotesize] [align=left] {{\small {\fontfamily{ptm}\selectfont 25\% FM}}};
+\draw (170.33,136) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 1000 U.T.M.}}};
+\draw (32.33,200) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
+\draw (273.81,160.5) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 60\% Expense}}};
+\draw (197,161.33) node  [font=\footnotesize] [align=left] {{\fontfamily{ptm}\selectfont {\small 40\% Credit}}};
+\draw (50.19,67.67) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
+\draw (127,66.5) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
+\draw (324.33,40) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
+\draw (188.57,79.67) node  [font=\footnotesize] [align=left] {{\small {\fontfamily{ptm}\selectfont 25\% FM}}};
+\draw (36.33,100) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
+\draw (281.62,63.5) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
+\draw (204.81,66) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
+\draw (168.33,38) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 1000 U.T.M.}}};
+\end{tikzpicture}
+
 Finally, the last modification is on April 14 2016, the second version of the law 20.900 modify articles 8 and 9 related to the limitations of donate to politics groups.
 
-A resume of the period of each law is in Table ~\ref{table: Table 1}
+A resume of the period of each law is in Table ~\ref{tabla: Table 1}
 
@@
 
-But, the changes in Chile don’t necessary match exactly with these cases, there is a limit of deduction but his changes through time are minors compared to others.
+But, the changes in Chile don’t necessary match exactly with these cases, there is a limit of deduction but his changes through time are minors compared to others and the data available between periods is not enough.
 The mayor changes are related to the monetary limit of donation that determinate the income deductibility.
@@
 
-The data used for this investigation is public from the records of The Ministry of Social Development, at the time that this paper is developed there are records from 2009 to 2018 in pdf format with a total of xx observations.
+The data used for this investigation is public from the records of The Ministry of Social Development, at the time that this paper is developed there are records from 2009 to 2016 in pdf format with a total of 1.549.354 observations.
 
@@
 Name of the project                    & Name of the project where de donation is made           \\
-Name of the institution or donator     & Institucional name or donator who receive the donation to a specific project     \\
+Name of the institution or donator     & Institutional name or donator who receive the donation to a specific project     \\
 Name of de donor                       & Name of the donor, it can be a natural person or a firm \\
@@
 }
+\caption{Attributes of data}
+\label{tabla: Table 2}
 \end{table}
 
-Each file contains one observation per donation registering different attributes of each donation, more information in Table XX.
-Nevertheless for the investigation we use only data from the period between xxx-xxx as we are going to look the effects of the change of the law 20.565 to 20.900, this contain approximate XX valid observations (footnote que es una observación valida, que tiene los datos de fecha y rut de donatario)
+Each file contains one observation per donation registering different attributes of each donation, more information in Table ~\ref{tabla: Table 2}.
+Nevertheless for the investigation we use only data from the period between january 2011 and april 2016 as we are going to look the effects of the change of the law 20.565 to 20.900, this contain approximate 1.517.769 valid observations^[We considered that a valid observation contain all information of each attribute, doesn't have unknown values]
 
@@
 
-As you can see in Figure XX it is plot the donations in time, each vertical line indicates the validity of a law (table XX), we can see that in period xx-xx there is an increase of the donation (number) and a change of the amount of the donation.
-Beside the changes of law related to the benefit of the donation there are also others changes that affect the records, one is the inclusion of the digital certificate that ease the process of donation for possibles donors, making it more easy to receive the benefits of the donation, this was implemented by some of the greater foundations in the country by 2013-2014.
+As you can see in Figure \@ref(fig:graficos_donaciones_1), Figure \@ref(fig:graficos_donaciones_2) and Figure \@ref(fig:graficos_donaciones_3) it is plot the donations in time of total amount of the donation, amount donated to the institution and the amount donated to the Mixed Found, each vertical line indicates the validity of a law (Table ~\ref{tabla: Table 1}), we can see that in period xx-xx there is an increase of the donation (number) and a change of the amount of the donation.
+
+Beside the changes of law related to the benefit of the donation, there are also others changes that affect the records.
+One is the inclusion of the digital certificate that ease the process of donation for possibles donors, making it more easy to receive the benefits of the donation, this was implemented by some of the greater foundations in the country by 2013-2014.
 Other important change in the same year was related to the obligatorily of inform to the minister the donations that was made to each institution, by that, the number of donation registered is more larger in 2014 than in years before.
 
-In Table XX there is a descriptive analysis of the donations in each period
+In Table \@ref(fig:tabla_resumen) there is a descriptive analysis of the donations in each period
 
-```{r, echo = FALSE,message=FALSE,warning = FALSE}
-#cargar base de datos 
-load("~/workspace/donationstax/Donaciones_total_graficos.Rdata")
-library(ggplot2)
-library(lubridate)
-library(stringr)
-
+```{r graficos_donaciones_1, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center",dev='png',dpi=200}
 #grafico con donaciones y cambio de leyes
@@
   ylim(0,20000)+
-  annotate("text", x = as.Date("2009-08-11"), y = 19000, label = "Law 19885")+
-  annotate("text", x = as.Date("2010-01-01"), y = 17000, label = "Law 20316")+
-  annotate("text", x = as.Date("2011-01-01"), y = 19000, label = "Law 20565")+
-  annotate("text", x = as.Date("2012-02-08"), y = 17000, label = "Law 20900_1")+
+  xlim(as.Date("2008-01-01"),as.Date("2018-12-31"))+
+  annotate("text", x = as.Date("2008-09-11"), y = 19500, label = "Law 19885")+
+  annotate("text", x = as.Date("2010-01-01"), y = 18000, label = "Law 20316")+
+  annotate("text", x = as.Date("2011-01-01"), y = 20000, label = "Law 20565")+
+  annotate("text", x = as.Date("2012-04-08"), y = 16000, label = "Law 20900_1")+
   annotate("text", x = as.Date("2016-04-14"), y = 19000, label = "Law 20900_2")+
   ggtitle("Donations: Total amount over time")
+
+```
+
+```{r graficos_donaciones_2, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center",dev='png',dpi=200}
 
@@
   ylim(0,20000)+
-  annotate("text", x = as.Date("2009-08-11"), y = 19000, label = "Law 19885")+
-  annotate("text", x = as.Date("2010-01-01"), y = 17000, label = "Law 20316")+
-  annotate("text", x = as.Date("2011-01-01"), y = 19000, label = "Law 20565")+
-  annotate("text", x = as.Date("2012-02-08"), y = 17000, label = "Law 20900_1")+
+  xlim(as.Date("2008-01-01"),as.Date("2018-12-31"))+
+  annotate("text", x = as.Date("2008-09-11"), y = 19500, label = "Law 19885")+
+  annotate("text", x = as.Date("2010-01-01"), y = 18000, label = "Law 20316")+
+  annotate("text", x = as.Date("2011-01-01"), y = 20000, label = "Law 20565")+
+  annotate("text", x = as.Date("2012-04-08"), y = 16000, label = "Law 20900_1")+
   annotate("text", x = as.Date("2016-04-14"), y = 19000, label = "Law 20900_2")+
@@
 
+```
+
+```{r graficos_donaciones_3, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center",dev='png',dpi=200}
 ggplot(Donaciones_total, aes(x = Fecha , y = monto_FM_UTM)) +
@@
   ylim(0,2500)+
-  xlim(as.Date("2008-11-30"),as.Date("2019-01-01"))+
-  annotate("text", x = as.Date("2009-03-11"), y = 2000, label = "Law 19885")+
-  annotate("text", x = as.Date("2010-01-01"), y = 1850, label = "Law 20316")+
-  annotate("text", x = as.Date("2011-01-01"), y = 2000, label = "Law 20565")+
-  annotate("text", x = as.Date("2012-02-08"), y = 1850, label = "Law 20900_1")+
+  xlim(as.Date("2008-01-01"),as.Date("2018-12-31"))+
+  annotate("text", x = as.Date("2008-09-11"), y = 2500, label = "Law 19885")+
+  annotate("text", x = as.Date("2009-11-01"), y = 2000, label = "Law 20316")+
+  annotate("text", x = as.Date("2011-01-01"), y = 2200, label = "Law 20565")+
+  annotate("text", x = as.Date("2012-04-08"), y = 1850, label = "Law 20900_1")+
   annotate("text", x = as.Date("2016-04-14"), y = 2000, label = "Law 20900_2")+
@@
 
-```{r, echo = FALSE,message=FALSE,warning = FALSE, results='asis'}
-#load()
-
-load("~/workspace/donationstax/Donaciones_total_graficos.Rdata")
-
-library(knitr)
-library(kableExtra)
-library(dplyr)
+```{r tabla_resumen, echo = FALSE,message=FALSE,warning = FALSE, results='asis',fig.align="center"}
 
@@
 kable(tabla.ley) %>%
-  kable_styling(bootstrap_options = "striped", position = "center",font_size = 8)
+  kable_styling(latex_options = c("striped", "scale_down"))
+  #kable_styling(bootstrap_options = "striped", position = "center",font_size = 6)
 
@@
 
-We use a pannel data regression (\ref{eq:1}) in order to study the effect of the change of law on the donations, and follow the next pannel structure
+We use a pannel data regression in order to study the effect of the change of law on the donations, and follow the next pannel structure
 
@@
 
-The result are the following
+In Table \@ref(fig:chunk-resumen_variables) there is a resume per variable of the main descriptive characteristics
 
-<!--tabla con los resultados de panel -->
+```{r resumen_variables, results='asis',echo = FALSE,message=FALSE,warning = FALSE,fig.align="center"}
+datos<-datos.seleccion
+colnames(datos)<-c("Donor ID","Amounto to MF (AMF)","Amount to institution (AI)","Donation Limit (DL)","Law 20900 (CL)",
+                   "Orden Donation (OD)","Accumulated Amount of Donor (AAD)","Accumulated Amount of Donee (AADo)",
+                   "Accumulated Amount to MF (AAMF)","Type Donor (TD)","Digital Certificate (DC)","Year")
+
+descr(datos)
+```
+
+The result of the pannel regression are the following
+
+```{r resultados_modelo, echo = FALSE,message=FALSE,warning = FALSE,fig.align="center", eval=FALSE}
+model <- readRDS("~/workspace/donationstax/iteraciones/model.RDS")
+library(sjPlot)
+library(sjmisc)
+library(sjlabelled)
+tab_model(model)
+
+#https://tex.stackexchange.com/questions/62492/what-is-the-correct-way-to-center-a-tikzpicture
+#https://cran.r-project.org/web/packages/sjPlot/vignettes/tab_model_estimates.html
+
+#print(summary(model))
+```
 

### 2020-09-01 article-elsevier/article-elsevier.Rmd
formateo figuras

@@
 ---
-title: More flexibility reduces social donations
+title: Flexibility reduces social donations
 author:
@@
 
-load("~/workspace/donationstax/Donaciones_total_graficos.Rdata")
-load("~/workspace/donationstax/iteraciones/Datos_seleccion_modelo.Rdata")
+load("~/workspace/donationstax/data_local/Donaciones_total_graficos.Rdata")
+load("~/workspace/donationstax/data_local/Datos_seleccion_modelo.Rdata")
 knitr::opts_chunk$set(fig.width=5, fig.height=5)
@@
 
-The law 19.885 (Fig (\ref{fig:law 19885})) concerning social donations in Chile in his first version on 2003, establishes a tributary benefit of 50\% of the donation as credit discount and the other 50\% consider as spending to make the donation.
+The law 19.885 (Fig (\ref{fig:law19885})) concerning social donations in Chile in his first version on 2003, establishes a tax benefit equivalent to 50\% of the donation amount as tax credit and the other 50\% consider as spending to make the donation.
 To receive this benefit the donor must donate a minimum of the 33\% of the donation to the Mixed Fund (MF^[It is a Fund created by the Law on Donations with Social Purposes to support initiatives that civil society organizations present and that directly benefit people in poverty and / or people with disabilities.
@@
 
+\begin{figure}[h]
+\label{fig:law19885}
 \tikzset{every picture/.style={line width=0.75pt}} 
@@
 \end{tikzpicture}
+\caption{19.885 law}
+\end{figure}
 

### 2021-11-16 article-elsevier/article-elsevier.Rmd
intento formato gráficos

@@
     footnote: 1
-  - name: Claudia Toledo-Aguirre
-    email: claudia.toledo@pucv.cl
-    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
+  # - name: Claudia Toledo-Aguirre
+  #   email: claudia.toledo@pucv.cl
+  #   affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
 #   - name: Cat Memes
@@
 
-load("~/workspace/donationstax/data_local/Donaciones_total_graficos.Rdata")
-load("~/workspace/donationstax/data_local/Datos_seleccion_modelo.Rdata")
+load("../data_local/Donaciones_total_graficos.Rdata")
+load("../data_local/Datos_seleccion_modelo.Rdata")
 knitr::opts_chunk$set(fig.width=5, fig.height=5)
@@
 
-```{r graficos_donaciones_1, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center",dev='png',dpi=200}
+```{r graficos_donaciones_1, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center", out.width="40%"}
 #grafico con donaciones y cambio de leyes
@@
 
-```{r graficos_donaciones_2, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center",dev='png',dpi=200}
+```{r graficos_donaciones_2, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center", out.width="40%"}
 
@@
 
-```{r graficos_donaciones_3, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center",dev='png',dpi=200}
+```{r graficos_donaciones_3, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="20%"}
 ggplot(Donaciones_total, aes(x = Fecha , y = monto_FM_UTM)) +
@@
   # Add labels
-  labs(x = "Date", y = "Donation to Mixed Found")+
+  labs(x = "Date", y = "Donation to Mixed Fund")+
   ylim(0,2500)+

### 2021-11-17 article-elsevier/article-elsevier.Rmd
corrige outputs para compilar

@@
 
-```{r graficos_donaciones_1, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center", out.width="40%"}
+```{r graficos_donaciones_1, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center", dev='png',dpi=200, out.width="70%"}
 #grafico con donaciones y cambio de leyes
@@
 
-```{r graficos_donaciones_2, echo = FALSE,message=FALSE,warning = FALSE, fig.align="center", out.width="40%"}
+```{r graficos_donaciones_2, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, dev='png', dpi=200, out.width="70%"}
 
@@
 
-```{r graficos_donaciones_3, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="20%"}
+```{r graficos_donaciones_3, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, dev='png', dpi=200, out.width="70%"}
 ggplot(Donaciones_total, aes(x = Fecha , y = monto_FM_UTM)) +

### 2021-11-19 code/ETL.R
ETL template

@@ -1,0 +1,56 @@
+# ETL
+## folder data_local should be created previously
+library(tidyverse)
+library(readxl)
+library(httr)
+# Required to install dataMeta latest version
+# library(devtools)
+# install_github("dmrodz/dataMeta")
+library(dataMeta)
+# XLS files path
+urls <- c("http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2010.xlsx",
+          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2011.xlsx",
+          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2012.xlsx",
+          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2013.xlsx",
+          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2014.xlsx",
+          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2015.xlsx",
+          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/09/Donaciones_2016.xlsx",
+          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2017.xlsx",
+          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2018.xlsx",
+          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2019.xlsx",
+          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/09/Donaciones_2020.xlsx")
+for (year in 2010:2019) {
+  # Temporary option
+  # GET(url1, write_disk(tf <- tempfile(fileext = ".xlsx")))
+  GET(urls[year-2009], write_disk(paste("data_local/d",year,".xlsx",sep="")))
+  print(paste("Year ",year," DOWNLOADED"))
+}
+
+d2020 = read_excel("data_local/d2020.xlsx",
+                   # Sheet name
+                   sheet = "Donaciones 2020", col_types = c("numeric", 
[…]

### 2021-12-16 Modelo metodologia.Rmd
Update methodology

---
title: "R Notebook"
output : html_notebook
---

Libreria
```{r}
library(tidyverse)
library(readxl)
library(httr)
# Required to install dataMeta latest version
# library(devtools)
# install_github("dmrodz/dataMeta")
library(dataMeta)
library(readr)
library(lubridate)
```

```{r}

df20 <- data.frame(institución20=c("AA", "aA", "Bb", " BB20", "CC(Pichilemu, O'Higgins)"),
                 proyecto=c('Project 1', 'ProjEct 2', "Project3", "projectoo 3", "pRoject4"),
                 donación=c(4, 7, 7, 8, 12))

dfSocial <- data.frame(InstitutionSocial=c("aa", "aa.", "bb", "cc "),
                 projectSocial=c("project1", "project2 region", "project3", "projectcuatro"),
                 donationSocial=c(4, 7, 15, 12))

```
Rename english + dictionario para merging U & original despues

```{r}
var_df20 <- names(df20)

names(df20) <- c("Institution", "Project", "Donation")

# Mark variables to describe their levels in detail
var_type20 <- c(0,0,0)
# Build Data Dictionary
linker20 <- build_linker(df20, variable_description = var_df20, variable_type = var_type20)

var_Social <- names(dfSocial)

names(dfSocial) <- c("Institution", "Project", "Donation")

# Mark variables to describe their levels in detail
var_typeSocial<- c(0,0,0)
# Build Data Dictionary
linkerSocial <- build_linker(dfSocial, variable_description = var_Social, variable_type = var_typeSocial)

```

Clean Data
_U = Unique

```{r}

df20$Institution_U <- toupper(df20$Institution)
df20$Project_U <- toupper(df20$Project)
df20[] <- lapply(df20, gsub, pattern = " ", replacement = "", fixed = TRUE) # no podemos hacer eso en verdad

levels(as.factor(df20$Institution_U)) # DosBB -> Hacer al mano
df20$Institution_U[df20$Institution_U=="BB20"]<-"BB"

levels(as.factor(df20$Project_U)) # hay dos proyectos 4 necesito de hacer al mano
df20$Project_U[df20$Project_U=="PROJECTOO3"]<-"PROJECT3"

dfSocial$Institution_U <- toupper(dfSocial$Institution)
dfSocial$Project_U <- toupper(dfSocial$Project)
dfSocial[] <- lapply(dfSocial, gsub, pattern = " ", replacement = "", fixed = TRUE)

levels(as.factor(dfSocial$Institution_U)) # DosBB -> Hacer al mano
dfSocial$Institution_U[dfSocial$Institution_U=="AA."]<-"AA"

### preguntar formula

levels(as.factor(dfSocial$Project_U)) # hay dos proyectos 4 necesito de hacer al mano
dfSocial$Project_U[dfSocial$Project_U=="projetcuatro"]<-"Project 4"

```
Quieremos solo un unico proyecto en el ejemplo no cambia nada
```{r}
dfSocial_U <- unique(dfSocial %>% select(Institution_U, Project_U, Donation))
df20_U <- unique(df20 %>% select(Institution_U, Project_U, Donation))

```

Merging los dos base de datos : Ni NA : Hacer al mano
```{r}
df_merge <- merge( dfSocial_U, df20_U, by=c("Project_U", "Institution_U"), all.x = T, all.y = T)

```
vigilar los errores, especialmente cuando hay NA, cambiar sur las bases antes del merg
Ex institution CC : CC(Pichilemu, O'Higgins)
```{r}

dfSocial_U$Project_U[dfSocial_U$Project_U=="PROJECT2REGION"]<-"PROJECT2"
dfSocial_U$Project_U[dfSocial_U$Project_U=="PROJECTCUATRO"]<-"PROJECT4"

df20_U$Institution_U[df20_U$Institution_U=="CC(PICHILEMU,O'HIGGINS)"]<-"CC"

# nuevo merg
df_merge <- merge( dfSocial_U, df20_U, by=c("Project_U", "Institution_U"), all.x = T, all.y = T)

```

Que hacer con el dictionario

### 2021-12-16 Modelo metodologia.Rmd
Final

@@
 ```
+
+Data
 
@@
 linker20 <- build_linker(df20, variable_description = var_df20, variable_type = var_type20)
+### HAcemos eso para definir los variable si persona tienne pregunta.
 
@@
 
-Que hacer con el dictionario
+```{r}
+dfSocial_UBis <- dfSocial
+df20_UBis <- df20
+
+```
+
+Merging los dos base de datos : Ni NA : Hacer al mano
+```{r}
+df_mergeBis <- merge( dfSocial_UBis, df20_UBis, by=c("Project_U", "Institution_U"), all.x = T, all.y = T)
+
+```
+vigilar los errores, especialmente cuando hay NA, cambiar sur las bases antes del merg
+Ex institution CC : CC(Pichilemu, O'Higgins)
+```{r}
+
+dfSocial_UBis$Project_U[dfSocial_UBis$Project_U=="PROJECT2REGION"]<-"PROJECT2"
+dfSocial_UBis$Project_U[dfSocial_UBis$Project_U=="PROJECTCUATRO"]<-"PROJECT4"
+
+df20_UBis$Institution_U[df20_UBis$Institution_U=="CC(PICHILEMU,O'HIGGINS)"]<-"CC"
+
+df_mergeBis <- merge( dfSocial_UBis, df20_UBis, by=c("Project_U", "Institution_U"), all.x = T, all.y = T)
+
+```
+Falta ano

### 2022-01-28 Modelo metodologia.Rmd
cambios antiguos pacha

@@
 ```{r}
-
 df20 <- data.frame(institución20=c("AA", "aA", "Bb", " BB20", "CC(Pichilemu, O'Higgins)"),
@@
                  donationSocial=c(4, 7, 15, 12))
-
 ```
@@
 linkerSocial <- build_linker(dfSocial, variable_description = var_Social, variable_type = var_typeSocial)
-
 ```
@@
 ```{r}
-
 df20$Institution_U <- toupper(df20$Institution)
@@
 
-### preguntar formula
+### TODO: preguntar formula
 
@@
 dfSocial$Project_U[dfSocial$Project_U=="projetcuatro"]<-"Project 4"
+```
 
-```
-Quieremos solo un unico proyecto en el ejemplo no cambia nada
+Queremos solo un unico proyecto en el ejemplo no cambia nada
 ```{r}
@@
 df20_U <- unique(df20 %>% select(Institution_U, Project_U, Donation))
-
 ```
@@
 df_merge <- merge( dfSocial_U, df20_U, by=c("Project_U", "Institution_U"), all.x = T, all.y = T)
-
 ```
@@
 ```{r}
-
 dfSocial_U$Project_U[dfSocial_U$Project_U=="PROJECT2REGION"]<-"PROJECT2"
@@
 df20_UBis <- df20
-
 ```
@@
 df_mergeBis <- merge( dfSocial_UBis, df20_UBis, by=c("Project_U", "Institution_U"), all.x = T, all.y = T)
-
 ```
@@
 ```{r}
-
 dfSocial_UBis$Project_U[dfSocial_UBis$Project_U=="PROJECT2REGION"]<-"PROJECT2"

### 2022-01-28 code/ETL.R

@@ -1,72 +1,99 @@
 # ETL
-## folder data_local should be created previously
+try(dir.create("data_local"))
 library(tidyverse)
 library(readxl)
-library(httr)
-# Required to install dataMeta latest version
-# library(devtools)
-# install_github("dmrodz/dataMeta")
-library(dataMeta)
-# Project data already consolidated
-library(readr)
+
 # Origen
 ## datasocial.ministeriodesarrollosocial.gob.cl/donaciones/proyectos/3
-projectsInfo <- read_delim("data_local/Donaciones_26112021105453.csv", 
-                           delim = ";", escape_double = FALSE, col_types = cols(`FECHA APROBACIÓN` = col_date(format = "%d/%m/%Y")), 
-                           trim_ws = TRUE, skip = 5)
+projectsInfo <- read_delim("data_local/Donaciones_26112021105453.csv",
+  delim = ";", escape_double = FALSE,
+  col_types = cols(`FECHA APROBACIÓN` = col_date(format = "%d/%m/%Y")),
+  trim_ws = TRUE, skip = 5
+)
+
 # XLS files path
-urls <- c("http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2010.xlsx",
-          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2011.xlsx",
-          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2012.xlsx",
-          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2013.xlsx",
-          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2014.xlsx",
-          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2015.xlsx",
-          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/09/Donaciones_2016.xlsx",
-          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2017.xlsx",
-          "http://sociedadcivil.ministeriodesarrollosocial.gob.cl/wp-content/uploads/2021/03/Donaciones_2018.xlsx",
[…]

### 2022-05-10 article-elsevier/article-elsevier.Rmd
cambios en ETL para replicar

@@
 
-#### Pannel data regression
-
-We want to study the effect on donations of the change of law of 20.565 to 20.900, the main change is that for the law 20.900 is no longer necessary to donor to at least two different institution an amount minor to 700 UTM (in Section XX number XX) making more easy to receive the economy incentive for donation, in order to that, is it expected that the donations raise (in number) but we don't now for sure what happens with the amount of the donations
-
-We use a pannel data regression in order to study the effect of the change of law on the donations, and follow the next pannel structure
+#### Panel data regression
+
+We want to study the effect on donations of the change of law of 20.565 to 20.900, the main change is that for the law 20.900 is no longer necessary to donor to at least two different institution an amount minor to 700 UTM (in Section XX number XX) making more easy to receive the economy incentive for donation, in order to that, is it expected that the donations raise (in number) but we don't now for sure what happens with the amount of the donation.
+
+We use a panel data regression in order to study the effect of the change of law on the donations, and follow the next pannel structure:
 

### 2022-05-10 presentation/presentation.Rmd
cambios en ETL para replicar

---
title: "Tax flexibility"
author: "Cea, Toledo"
date: "1/8/2020"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::include_graphics
#http://sociedadcivil.ministeriodesarrollosocial.gob.cl/calculo-beneficio-tributario/
```

## Variables creadas

Según lo acordado en la última reunión se definen las siguientes variables:

| Variable 	| Tipo 	| Definición 	|
|:-:	|:-:	|:-:	|
| Limite.donacion 	| Dicotómica (factor) 	| 1 si la suma de las donaciones del donante en aquel año es mayor a 1000 UTM, 0 eoc 	|
| Ley.20900 	| Dicotómica (factor) 	| 1 si la fecha de la donación es mayor a 2012-02-08, fecha de inicio de vigencia de la ley 20.900, 0 eoc 	|
| Orden.donacion 	| Entera (integer) 	| Toma valor según la posición ordinal de la donación en el año de aquel donante 	|
| Monto_acum_donante 	| Numérica (double) 	| Monto acumulado hasta la presente donación por el donante en el año (incluyendo la actual) 	|
| Monto_acum_donatario 	| Numérica (double) 	| Monto acumulado hasta la presente donación por el donatario en el año (incluyendo la actual) 	|
| Contribuyente_1ra 	| Dicotómica (factor) 	| 1 si el contribuyente es de primera categoría, 0 eoc 	|

Para generar las variables se ejecuta el siguiente código sobre aquellas donaciones contenidas en el periodo de analisis ("2011-01-01" y "2016-04-13"), en donde se conozca el RUT del donante

```{r echo=TRUE, eval=FALSE}
#cargar BD
load("~/SxC-ETL/Donaciones/DonacionesFM/modelo articulo/Donaciones_final_20julio.Rdata")
datos.modelo$ID<-seq(1,nrow(datos.modelo))
datos.modelo$Limite.donacion<-NA
datos.modelo$Ley.20900<-NA
datos.modelo$Orden.donacion<-NA
datos.modelo$Mondo_acum_donante<-NA
datos.modelo$Mondo_acum_donatario<-NA
datos.modelo$Contribuyente_1ra<-NA

library(lubridate)
fecha_limite=ymd("2012-02-08") #fecha ley 20900
for(j in 1:nrow(datos.modelo)){ #
  print(j)
  donante<-as.data.frame(matrix(ncol=19))
  donatario<-as.data.frame(matrix(ncol=19))

  donante<-datos.modelo.final[datos.modelo.final$RUT==datos.modelo.final[j,9],] #selección de df solo con las donaciones del donante
  donatario<-datos.modelo.final[datos.modelo.final$DONATARIO==datos.modelo.final[j,3],] #selección de df solo con donaciones a donatario

  #Limite_donacion
  #suma de las donaciones del año mayor a 1000
  #extraer año de la donación 
  año.don<-year(datos.modelo.final[j,7])
  donante$año<-year(donante$FECHA)
  datos.modelo.final[j,14]<-ifelse(sum(subset(donante,año==año.don)$monto.total_UTM,na.rm = TRUE)>1000 ,1,0) #si el monto total es mayor a 1000 entonces 1
  #ley 20900
  datos.modelo.final[j,15]<-ifelse(datos.modelo.final[j,7]>=fecha_limite,1,0) #si la fecha de la donación es dentro del periodo de la ley entonces 1
  #orden donacion 
  donante<-subset(donante,año==año.don)
  donante<-donante[order(donante$FECHA),]
  rownames(donante)<-NULL
  datos.modelo.final[j,16]<- which(donante$ID == datos.modelo.final[j,13]) #lugar/posición de la donación
  #monto acumulado del donante
  datos.modelo.final[j,17]<-sum(donante[1:datos.modelo.final[j,16],]$monto.total_UTM,na.rm = TRUE)
  #monto donacion donatario
  donatario$año<-year(donatario$FECHA)
  donatario<-subset(donatario,año==año.don)
  donatario<-donatario[order(donatario$FECHA),]
  rownames(donatario)<-NULL
  orden.don<- which(donatario$ID == datos.modelo.final[j,13])
  #monto acumulado del donante
  datos.modelo.final[j,18]<-sum(donatario[1:orden.don,]$monto.total_UTM,na.rm = TRUE)
  #contribuyente promera categoria
  datos.modelo.final[j,19]<-ifelse(datos.modelo.final[j,9]>49000000,1,0) #1 si es de primera categoria 
}

```

Se actualiza el tipo de variable

```{r echo=TRUE, eval=FALSE}
#cambiar tipo de variables 
datos.modelo.final$Limite.donacion<-as.factor(datos.modelo.final$Limite.donacion)
datos.modelo.final$Ley.20900<-as.factor(datos.modelo.final$Ley.20900)
datos.modelo.final$Orden.donacion<-as.integer(datos.modelo.final$Orden.donacion)
datos.modelo.final$Mondo_acum_donante<-as.double(datos.modelo.final$Mondo_acum_donante)
datos.modelo.final$Mondo_acum_donatario<-as.double(datos.modelo.final$Mondo_acum_donatario)
datos.modelo.final$Contribuyente_1ra<-as.factor(datos.modelo.final$Contribuyente_1ra)
```

## Resumen de variables

```{r , echo = FALSE, results = 'asis',message=FALSE,warning = FALSE}
library(summarytools)
st_css()
load("~/SxC-ETL/Donaciones/DonacionesFM/modelo articulo/Donaciones_final_0108_ver2.Rdata")
#ordenar columnas
datos.modelo.final = datos.modelo.final [ , c(1,2,3,4,5,6,7,9,10,11,12,13,8,14,15,16,17,18,19)]

print(dfSummary(datos.modelo.final[,13:19], plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp"), method = 'render',na.col=FALSE)

```
## Resumen de variables 2

```{r , echo = FALSE, results = 'asis',message=FALSE,warning = FALSE}
library(summarytools)
st_css()
load("~/SxC-ETL/Donaciones/DonacionesFM/modelo articulo/Donaciones_final_0108_ver2.Rdata")
datos.modelo.final = datos.modelo.final [ , c(1,2,3,4,5,6,7,9,10,11,12,13,8,14,15,16,17,18,19)]
descr(datos.modelo.final[,13:19], style = 'rmarkdown')
print(freq(datos.modelo.final$Limite.donacion), method = 'render')
print(freq(datos.modelo.final$Ley.20900), method = 'render')
print(freq(datos.modelo.final$Contribuyente_1ra), method = 'render')

```

## Modelo de regresión de panel

```{r , echo = TRUE,message=FALSE,warning = FALSE,eval=FALSE}
load("~/SxC-ETL/Donaciones/DonacionesFM/modelo articulo/Donaciones_final_0108_ver2.Rdata")
library(panelr)
library(lubridate)
datos.modelo.final$año<-year(datos.modelo.final$FECHA)
datos.seleccion<-subset(datos.modelo.final,select =c("monto.total_UTM","RUT.DONANTE","año","Limite.donacion"
                                                     ,"Ley.20900","Orden.donacion"          
                                                     ,"Mondo_acum_donante","Mondo_acum_donatario",
                                                     "Contribuyente_1ra"))
regresion <- panel_data(datos.seleccion, id = RUT.DONANTE, wave = año)
regresion
#dv ~ varying_variables | invariant_variables | cross_level_interactions/random effects
model <- wbm(monto.total_UTM ~ Limite.donacion+Orden.donacion+Mondo_acum_donante+Mondo_acum_donatario |
               Ley.20900 + Contribuyente_1ra | 
               ( año| RUT.DONANTE), data = regresion)
summary(model)

save(model,file="modeloPR0208.Rdata")

```

```{r echo=TRUE}

load("~/SxC-ETL/Donaciones/DonacionesFM/modelo articulo/modeloPR0208.Rdata")
summary(model)

```

### 2022-05-10 BD_modelo.R

@@ -2,6 +2,11 @@
 
 #### Montos en UTM ####
 #cargar BD
+
+# TODO: CARGAR INPUTS EN GOOGLE DRIVE
+
+# TODO: CRUCE CON SINIM GEOREFERENCIADO
+
 ScriptsPath_ETL.consolidacion<-paste("/home/",usuario,"/workspace/SxC_ETL/Donaciones/DonacionesFM/Consolidacion/",sep="")
 load(paste(ScriptsPath_ETL.consolidacion,"Donaciones_total_compilado_070820.Rdata",sep=""))
 
@@ -10,6 +15,9 @@ Donaciones_total<-df2
 Donaciones_total<-Donaciones_total[!is.na(Donaciones_total$RUT),] #1.540.636
 
 library(readxl)
+
+# TODO: TRABAJAR TODO EN UTM
+
 valorUTM <- read_excel("~/workspace/donationstax/valorUTM.xlsx")
 colnames(valorUTM)<-c("Año","Mes","UTM")
 
@@ -125,6 +133,9 @@ for(j in  1:nrow(datos.modelo)){ #
   datos.modelo[j,15]<-ifelse(datos.modelo[j,3]>=fecha_cert.digital,1,0) #si la fecha de la donación 
   #es dentro del periodo de vigencia del cert digital entonces 1
 }
+
+
+# TODO: ESTO USABA TABULA, EL XLSS GENERA LO MISMO
 
 #unir distintas BD generadas 
 #5 BD generadas en MacBook Claudia

### 2022-05-10 code/ETL.R

@@ -5,6 +5,8 @@ library(readxl)
 
 # Origen
 ## datasocial.ministeriodesarrollosocial.gob.cl/donaciones/proyectos/3
+
+# TODO: PARA EL DICCIONARIO, MATCH NO PERFECTO
 projectsInfo <- read_delim("data_local/Donaciones_26112021105453.csv",
   delim = ";", escape_double = FALSE,
   col_types = cols(`FECHA APROBACIÓN` = col_date(format = "%d/%m/%Y")),
@@ -85,6 +87,9 @@ linker <- build_linker(d2020, variable_description = var_desc, variable_type = v
 # Standarization of variables
 ## Institution names
 ### 2020: Looks good!
+
+# REVISAR ESTO: DICCIONARIO INSTITUCION-PROYECTO
+
 institutionName <- d2020 %>%
   select(institutionName) %>%
   distinct()
@@ -92,7 +97,7 @@ institutionName <- d2020 %>%
 ## Project names
 projectName <- d2020 %>%
   select(projectName, institutionName) %>%
-  distinct()
+  distinct() # TODO: DICCIONARIO
 
 names(projectName) <- c("nameOLD", "institution")
 

### 2022-05-10 article-elsevier/article-elsevier.tex
permisos

\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

  \journal{Economics Letters or Journal of Public Economics} % Sets Journal name

\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={More flexibility reduces social donations},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}

% Pandoc header

\begin{document}
\begin{frontmatter}

  \title{More flexibility reduces social donations}
    \author[School of Industrial Engineering, Pontificia Universidad Católica de
Valparaíso]{Sebastián Cea-Echenique\corref{1}}
   \ead{sebastian.cea@pucv.cl} 
    \author[School of Industrial Engineering, Pontificia Universidad Católica de
Valparaíso]{Claudia Toledo}
   \ead{claudia@example.com} 
        \cortext[1]{Corresponding Author}

  \begin{abstract}
  We exploit a change in tax donations' law to evaluate a change to more
  flexibility.
  \end{abstract}

 \end{frontmatter}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{motivation-and-legal-background}{%
\paragraph{Motivation and legal
background}\label{motivation-and-legal-background}}

Law XX introduced a framework to foster social donations. Several
changes to that law were made\ldots{}

\hypertarget{insertion-in-the-literature}{%
\paragraph{Insertion in the
Literature}\label{insertion-in-the-literature}}

The relation between taxes and social donations has been studied in the
recent literature by \ldots{}

\hypertarget{empirical-strategy}{%
\section{Empirical strategy}\label{empirical-strategy}}

We use a differences in differences approach in a panel structure of the
data.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\end{document}

### 2022-05-10 code/ETL.R
sketch rpkg

@@ -2,6 +2,7 @@
 try(dir.create("data_local"))
 library(tidyverse)
 library(readxl)
+library(dataMeta)
 
 # Origen
 ## datasocial.ministeriodesarrollosocial.gob.cl/donaciones/proyectos/3
@@ -79,8 +80,8 @@ var_type <- c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1)
 linker <- build_linker(d2020, variable_description = var_desc, variable_type = var_type)
 
 ## The following does not work
-## dict <- build_dict(d2020, linker = linker, option_description = NULL,
-##                   prompt_varopts = FALSE)
+# dict <- build_dict(d2020, linker = linker, option_description = NULL,
+#                   prompt_varopts = FALSE)
 ## Error in FUN(X[[i]], ...) :
 ## only defined on a data frame with all numeric variables
 

### 2022-05-10 donationstax-rpkg/dev/tidy_data.R

@@ -1,0 +1,31 @@
+library(dplyr)
+library(readxl)
+library(purrr)
+library(lubridate)
+library(stringr)
+library(glue)
+library(janitor)
+
+finp <- sprintf("~/github/donationstax/data_local/d%s.xlsx", 2010:2020)
+
+d_2010_2014 <- map_df(
+  finp[1:4],
+  function(x) {
+    message(x)
+    read_excel(x,
+               col_types = c("numeric", "text", "text",
+                             "text", "text", "numeric", "numeric",
+                             "numeric")) %>%
+      clean_names()
+  })
+
+d_2010_2014 <- d_2010_2014 %>%
+  mutate(
+    fecha = case_when(
+      nchar(fecha) == 5 ~ as.character(as.Date(as.numeric(fecha), origin = "1900-12-30")),
+      nchar(fecha) == 10 ~ paste(str_sub(fecha, 7, 10), str_sub(fecha, 4, 5), str_sub(fecha, 1, 2), sep = "-")
+    )
+  )
+
+d_2010_2014 <- d_2010_2014 %>%
+  mutate(fecha = as_date(fecha))

### 2022-05-10 donationstaxrpkg/dev/tidy_data.R

@@ -1,0 +1,33 @@
+library(dplyr)
+library(readxl)
+library(purrr)
+library(lubridate)
+library(stringr)
+library(glue)
+library(janitor)
+
+finp <- sprintf("~/github/donationstax/data_local/d%s.xlsx", 2010:2020)
+
+d_2010_2014 <- map_df(
+  finp[1:4],
+  function(x) {
+    message(x)
+    read_excel(x,
+               col_types = c("numeric", "text", "text",
+                             "text", "text", "numeric", "numeric",
+                             "numeric")) %>%
+      clean_names()
+  })
+
+d_2010_2014 <- d_2010_2014 %>%
+  mutate(
+    fecha = case_when(
+      nchar(fecha) == 5 ~ as.character(as.Date(as.numeric(fecha), origin = "1900-12-30")),
+      nchar(fecha) == 10 ~ paste(str_sub(fecha, 7, 10), str_sub(fecha, 4, 5), str_sub(fecha, 1, 2), sep = "-")
+    )
+  )
+
+d_2010_2014 <- d_2010_2014 %>%
+  mutate(fecha = as_date(fecha))
+
+use_data(d_2010_2014)

### 2022-05-10 donationstaxrpkg/dev/tidy_data.R
hasta 2014 ordenado

@@ -21,13 +21,26 @@ d_2010_2014 <- map_df(
 
 d_2010_2014 <- d_2010_2014 %>%
   mutate(
-    fecha = case_when(
+    fecha2 = case_when(
       nchar(fecha) == 5 ~ as.character(as.Date(as.numeric(fecha), origin = "1900-12-30")),
       nchar(fecha) == 10 ~ paste(str_sub(fecha, 7, 10), str_sub(fecha, 4, 5), str_sub(fecha, 1, 2), sep = "-")
     )
   )
 
 d_2010_2014 <- d_2010_2014 %>%
-  mutate(fecha = as_date(fecha))
+  mutate(
+    fecha2 = ifelse(fecha == "31-11-2011", "2011-11-30", fecha2),
+    fecha2 = ifelse(fecha == "31/09/2011", "2011-09-30", fecha2),
+    fecha2 = ifelse(fecha == "31/11/2011", "2011-11-30", fecha2),
+    fecha2 = ifelse(fecha == "Nov. 2012", "2012-11-30", fecha2),
+    fecha2 = ifelse(fecha == "Dic. 2012", "2012-12-31", fecha2),
+    fecha2 = ifelse(fecha == "2301-2013", "2013-01-23", fecha2)
+  )
 
-use_data(d_2010_2014)
+d_2010_2014 <- d_2010_2014 %>%
+  mutate(fecha2 = as_date(fecha2))
+
+d_2010_2014 %>%
+  filter(is.na(fecha2))
+
+use_data(d_2010_2014, overwrite = T)

### 2022-05-10 donationstax-rpkg/dev/tidy_data.R
donations pkg

@@ -1,31 +1,0 @@
-library(dplyr)
-library(readxl)
-library(purrr)
-library(lubridate)
-library(stringr)
-library(glue)
-library(janitor)
-
-finp <- sprintf("~/github/donationstax/data_local/d%s.xlsx", 2010:2020)
-
-d_2010_2014 <- map_df(
-  finp[1:4],
-  function(x) {
-    message(x)
-    read_excel(x,
-               col_types = c("numeric", "text", "text",
-                             "text", "text", "numeric", "numeric",
-                             "numeric")) %>%
-      clean_names()
-  })
-
-d_2010_2014 <- d_2010_2014 %>%
-  mutate(
-    fecha = case_when(
-      nchar(fecha) == 5 ~ as.character(as.Date(as.numeric(fecha), origin = "1900-12-30")),
-      nchar(fecha) == 10 ~ paste(str_sub(fecha, 7, 10), str_sub(fecha, 4, 5), str_sub(fecha, 1, 2), sep = "-")
-    )
-  )
-
-d_2010_2014 <- d_2010_2014 %>%
-  mutate(fecha = as_date(fecha))

### 2022-05-10 donationstaxrpkg/README.Rmd

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# donationstaxrpkg

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/donationstaxrpkg)](https://CRAN.R-project.org/package=donationstaxrpkg)
<!-- badges: end -->

The goal of donationstaxrpkg is to ...

## Installation

You can install the development version of donationstaxrpkg from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ingUANDES/donationstax")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(donationstaxrpkg)
## basic example code
```

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
